### 2022-02-06 outputs/paper/paper.Rmd
final commit

---
title: "Who was most affected by COVID-19 in Toronto"
author: 
  - Lantao Cui
thanks: "Code and data are available at: https://github.com/cuilantao/STA304-Paper1."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "The first COVID-19 case was reported on 31 December 2019, exactly two years from now. At first, everyone thought that this is nothing but a seasonal flu and it will end in less than a month, however, it turned out to be a global pandemic and has taken numerous people's lives. In this paper, We obtain and analyze all reported COVID-19 cases in the city of Toronto. We found out that COVID-19 is more fatal toward elders and hits hardest on communities with low income or high population density. Our findings will help the city of Toronto to better help those people at needs."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(kableExtra)
wd <- getwd()
wd
setwd("../..")
covid19_cases_cleaned <- read_csv("inputs/data/COVID19-cases-clean.csv")
```

# Introduction
Ever since the dawn of civilization, humanity had been fighting against different plagues. The earliest recorded pandemic happened during the
Peloponnesian war, which is almost 3000 years from now. This plague wiped through all of Libya, Ethiopia and Egypt, killed almost two-thirds of 
the entire population. Another well known plague is the black death, which lasted for decades and was responsible for the death of nearly one-thirds of the World Population. But after the industrial revolution, the technology advanced so fast and people developed the illusion that we should be able to defeat any kinds of plague. Therefore, nobody cared at all when COVID first started, until it started to take away millions of people's lives.

To find out who was most affected, we obtained all of COVID-19 case reports from the City of Toronto's data portal. After some investigation, we found out that as the patient's age increases, the mortality and hospitalization rate also increases exponentially. The mortality rate of kids under 19 years old is 0.00007 and this number increases to 0.23 for people above 90 years old, by a factor of 3000. On top of that, low income or high density neighbourhood are hit the hardest during this pandemic. Among 140 different communities, the top 10 communities with the most COVID-19 cases have contributed 20% of Toronto's total COVID-19 cases.

Our findings have lots of implications, it identifies the groups of people and neighborhood that are most affected by COVID-19, this information will allow the government to better support them and come up with new proceudres that will
slow down the spread of COVID-19.

# Data
## Data Source
This dataset contains all of the data reported to Toronto Public Health and are gathered through an R package called "opendatatoronto" [@opendatator]. This dataset contains all of the demographic, geographic, and severity information for all of the confirmed and potential cases of COVID-19. It's updated on a weekly basis and was last updated on Feb 2, 2022.

## Data Collection and Methodology
All of COVID-19 cases are reported to Toronto Public Health by local testing laboratories, then Open data toronto collect those data from the provincial Case & Contact Management System. The strength of this dataset is that it is very detailed and contains a lot of valuable information, for instance, for every reported case, this dataset will track it and include the final result. This can help us to analyze the mortality rate of COVID-19 on different age groups. However, although the dataset contains all of the reported cases, it can not be viewed as 
an accurate measure of the actual COVID-19 cases because of various reasons. The most notable problem is that you have to get tested to be officially diagnosed with COVID-19. This leads to several problems, first of all, COVID-19 has similar symptoms as a seasonal flu or a common cold, so some people will refuse to get tested. Another problem is the shortage of testing kits, according to the Ontario Government, due to the fast spread of the Omicron variant, PCR tests are only available to "high-risk individuals and individuals who work at high-risk settings". Therefore, those numbers should only be interpreted as "an underestimate of the true number of individuals with COVID-19 in Toronto".

## Data overview
This dataset contains all of the demographic, geographic, and severity data of the reported COVID-19 cases in City of Toronto. It has a total of 272017 cases and has 18 attributes. The first two attributes serves as an identical identifier and are removed in the data pre-processing step. The
next 5 attributes contain information about the age of the patient, their source of infection and the neighborhood they live in. The next 5 columns are about the gender of the patient, whether case is probable or confirmed, and the outcome. The final 6 columns help to assess the severity of the case. To get a better understanding of the actual data, let us take a look at Figure 1, which is a sample view of the data and is produced by R [@citeR];

```{r echo=FALSE}
head(covid19_cases_cleaned)
```
## The effect of COVID-19 on different age groups
People always have the illusion that younger people are less affected from disease because they have a stronger immune system. However, this is not always the case, during the 1918 flu, millions of healthy young people died, this is because the 1918 flu triggered a cytokine storm. Basically this will turn your own immune system against you, so there are less deaths in older and middle-aged adults because they have a weaker immune system. Figure 1 made by ggplot2[@plot], Table 1 made by KableExtra [@kabel] and Knitr [@knitr] shows total number of confirmed COVID-19 cases among each group, and the severity of those COVID-19 cases.

```{r,include = FALSE}
# first find out which age group has the most reported covid 19 cases
covid_combined_by_age_group <-
  group_by(covid19_cases_cleaned, `Age Group`) %>%
  summarize(n())
names(covid_combined_by_age_group)[names(covid_combined_by_age_group) == 'n()'] <- 'Total Covid Cases'

fatal_covid_cases <- covid19_cases_cleaned %>% filter(`Outcome` == 'FATAL')
fatal_covid_case_combined_by_age_group <- fatal_covid_cases %>% 
  group_by(`Age Group`) %>% 
  summarize(n())
names(fatal_covid_case_combined_by_age_group)[names(fatal_covid_case_combined_by_age_group) == 'n()'] <- 'Fatal Cases'

total_case_and_fatal_case <- merge(covid_combined_by_age_group,fatal_covid_case_combined_by_age_group,by="Age Group")
total_case_and_fatal_case$Mortality_Rate <- with(total_case_and_fatal_case, round(`Fatal Cases` / `Total Covid Cases`, 5))

# ICU cases
cases_that_went_to_hospital <- covid19_cases_cleaned %>% filter(`Ever Hospitalized` == 'Yes');
cases_that_went_to_hospital_combined_by_age_group <- cases_that_went_to_hospital %>% 
  group_by(`Age Group`) %>%
  summarize(n())
names(cases_that_went_to_hospital_combined_by_age_group)[names(cases_that_went_to_hospital_combined_by_age_group) == 'n()'] <- 'Hospitalized'
total_case_fatal_hos <- merge(total_case_and_fatal_case, cases_that_went_to_hospital_combined_by_age_group, by = "Age Group")
total_case_fatal_hos$Hospital_Rate <- with(total_case_fatal_hos, round(`Hospitalized` / `Total Covid Cases`, 5))
total_case_fatal_hos
```

```{r , fig.cap="Effect of COVID-19 on different Age Group", echo=FALSE, warning=FALSE, message = FALSE}
total_case_fatal_hos %>%
  knitr::kable(caption = "Effect of COVID-19 on different Age Group", 
               col.names = c("Age Group", "Total COVID-19 Cases", "Fatal Cases", "Mortality Rate", "Hospitalized", "Hospitalized Rate"),
               align = c('l', 'l', 'l', 'l', 'l', 'l'),
               booktabs = T) %>%
  kable_styling(full_width = T, latex_options = "hold_position")
```

```{r include = FALSE}
age_group_without_case_count <- subset( total_case_and_fatal_case, select = -c(`Total Covid Cases`, `Fatal Cases` ))
age_group_without_case_count$Type <- "Mortality Rate"
names(age_group_without_case_count)[names(age_group_without_case_count) == 'Mortality_Rate'] <- 'Rate'
another_frame <- subset(total_case_fatal_hos, select = -c(`Total Covid Cases`, `Fatal Cases`, `Hospitalized`, `Mortality_Rate`))
names(another_frame)[names(another_frame) == 'Hospital_Rate'] <- 'Rate'
another_frame$Type <- "Hospitalized Rate"
new <- rbind(age_group_without_case_count, another_frame)
new$`Age Group`[new$`Age Group`=="19 and younger"] <- "19 and younger"
new$`Age Group`[new$`Age Group`=="20 to 29 Years"] <- "20-29"
new$`Age Group`[new$`Age Group`=="30 to 39 Years"] <- "30-39"
new$`Age Group`[new$`Age Group`=="40 to 49 Years"] <- "40-49"
new$`Age Group`[new$`Age Group`=="50 to 59 Years"] <- "50-59"
new$`Age Group`[new$`Age Group`=="60 to 69 Years"] <- "60-69"
new$`Age Group`[new$`Age Group`=="70 to 79 Years"] <- "70-79"
new$`Age Group`[new$`Age Group`=="80 to 89 Years"] <- "80-89"
new$`Age Group`[new$`Age Group`=="90 and older"] <- "Above 90"
```

```{r, fig.cap="Effect of COVID-19 on different Age Groups", echo=FALSE, warning=FALSE, message = FALSE, fig.width=8, fig.height=3}
ggplot(new, aes(x=`Age Group`, y=`Rate`,group = `Type`, color = `Type`)) +
    geom_line()
```

From the figure and table, it's clear that there is some correlation between people's age and the effect of COVID-19. As people's age increase, the mortality and hospitalization rate grow almost exponentially, the mortality rate of kid under 19 years old is 0.00007, but this number increases to 0.23 when the person is older than 90, which is a factor of 3285. Study shows that "adults over 65 years of age represent 80% of hospitalizations and have a 23-fold greater risk of death than those under 65" [@mueller]. The reason for this is that as people ages, their immune system function will gradually decline, which makes them more vulnerable to virus. Another reason is that older people are more likely to have underlying health conditions such as diabetes and high blood pressure. Those health condition will worsen the symptom of COVID-19 and make it more fatal.

## The effect of COVID-19 on different communities in Toronto
The next thing we will explore is the effect of COVID-19 on different communities in Toronto. After grouping by and sorting the data using R [@citeR], Figure 2 are produced with ggplot2 [@plot]. The figure plots the top 10 communities with the most COVID-19 infections, a quick research shows those are mostly low-income communities or neighborhood that has a large population density. This is because most jobs with low income require the worker to have much more in-person interactions with other people, thus increasing the risk of COVID-19 infection. And a high density neighborhood usually has a lot of apartment buildings, and it's relatively easier for the virus to spread within an apartment building because people are sharing lots of things such as air vent and elevator. This finding shows that COVID-19 situations varies across different communities and it maybe beneficial if the government starts to enforce different procedure based on different communities.

```{r, include = FALSE}
covid_combined_by_postal_code <-
  group_by(covid19_cases_cleaned, `Neighbourhood Name`) %>%
  summarize(n())
names(covid_combined_by_postal_code)[names(covid_combined_by_postal_code) == 'n()'] <- 'n'
```

```{r, include = FALSE}
total_case_by_postal_sorted <- covid_combined_by_postal_code[order(-covid_combined_by_postal_code$n),]
total_case_by_postal_sorted
top_10 <- total_case_by_postal_sorted[1:10, ]
top_10
```

\pagebreak
```{r, fig.cap="Effect of COVID-19 on different communities", echo=FALSE, warning=FALSE, message = FALSE, fig.width=10, fig.height=4}
ggplot(data=top_10, aes(x = reorder(`Neighbourhood Name`, n), y=n)) +
  geom_bar(stat="identity", position=position_dodge()) + coord_flip()
```

\pagebreak

# References

### 2022-02-06 scripts/01-data_download.R

@@ -1,0 +1,30 @@
+#### Preamble ####
+# Purpose: Download data from opendatatoronto 
+# Author: Lantao Cui
+# Data: 31 January 2021
+# Contact: lantao.cui@mail.utoronto.ca
+# License: MIT
+
+#### Workspace setup ####
+library(opendatatoronto)
+library(tidyverse)
+library(dplyr)
+
+#### Data download ####
+# https://open.toronto.ca/dataset/covid-19-cases-in-toronto/
+
+# Data set are grouped into packages that have multiple datasets that are 
+# relevant to that topic. So we can obtain the package using a unique key.
+# get package
+package <- show_package("64b54586-6180-4485-83eb-81e8fae3b8fe")
+package
+
+# get all resources for this package
+resources <- list_package_resources("64b54586-6180-4485-83eb-81e8fae3b8fe")
+
+datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))
+
+# let's load all covid cases
+all_covid_cases <- filter(datastore_resources, row_number()==1) %>% get_resource()
+write_csv(all_coivd_cases, "inputs/data/COVID19-cases.csv")
+

### 2022-02-06 scripts/02-data_preprocessing.R

@@ -1,0 +1,31 @@
+#### Preamble ####
+# Purpose: Preprocess the data for future analyze
+# Author: Lantao Cui
+# Data: 31 January 2021
+# Contact: lantao.cui@mail.utoronto.ca
+# License: MIT
+
+#### load the libraies we need ####
+library(tidyverse)
+library(dplyr)
+
+#### Read the csv files ####
+city_of_toronto_covid_cases <- read_csv("inputs/data/COVID19-cases.csv")
+
+
+#### Remove the ID column, we don't need them for the analyze ####
+city_of_toronto_covid_cases_clean <- city_of_toronto_covid_cases[-c(1,2)]
+
+#### Let's find out if there are any NAs in this dataset ####
+number_of_nas <- sum(is.na(city_of_toronto_covid_cases_clean))
+
+
+#### We found out that there are NA values, so we should remove them as they will affect the data analyze ####
+covid_case_with_na_remove <- na.omit(city_of_toronto_covid_cases_clean)
+
+#### Double check that there is no more NA values ####
+stopifnot(sum(is.na(covid_case_with_na_remove)) == 0)
+
+#### Now we can save the cleaned data ####
+write_csv(covid_case_with_na_remove,"inputs/data/COVID19-cases-clean.csv")
+

### 2022-02-07 outputs/paper/paper.Rmd
done

@@
 
-```{r setup, include=FALSE}
+```{r setup, include = FALSE}
 knitr::opts_chunk$set(echo = TRUE)
@@
 covid19_cases_cleaned <- read_csv("inputs/data/COVID19-cases-clean.csv")
+head(covid19_cases_cleaned)
 ```
@@
 
+## Conclusion
+Our findings clearly revealed that COVID-19 hits certain people and neighborhood really hard and they require more attention from the government.
+Luckily, the City of Toronto is aware of this situation and have launched support programs
+targeting those neighborhood.
+For instance, the City of Toronto is offering free self-isolation sites for those people diagnosed with COVID-19 and is also giving seniors and people with underlying health condition top priority in the vaccination program.
+
 \pagebreak

### 2022-02-07 scripts/01-data_download.R

@@ -5,16 +5,13 @@
 # Contact: lantao.cui@mail.utoronto.ca
 # License: MIT
 
+
+## Opendata toronto's get_resource function sometimes doesnt work and return code 500. If this happens, please go to https://open.toronto.ca/dataset/covid-19-cases-in-toronto/ and manually download the data,
+## then put it inside inputs/data/COVID19-cases.csv. Thank you!
 #### Workspace setup ####
 library(opendatatoronto)
-library(tidyverse)
 library(dplyr)
 
-#### Data download ####
-# https://open.toronto.ca/dataset/covid-19-cases-in-toronto/
-
-# Data set are grouped into packages that have multiple datasets that are 
-# relevant to that topic. So we can obtain the package using a unique key.
 # get package
 package <- show_package("64b54586-6180-4485-83eb-81e8fae3b8fe")
 package
@@ -22,9 +19,10 @@ package
 # get all resources for this package
 resources <- list_package_resources("64b54586-6180-4485-83eb-81e8fae3b8fe")
 
+# identify datastore resources; by default, Toronto Open Data sets datastore resource format to CSV for non-geospatial and GeoJSON for geospatial resources
 datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))
 
-# let's load all covid cases
-all_covid_cases <- filter(datastore_resources, row_number()==1) %>% get_resource()
-write_csv(all_coivd_cases, "inputs/data/COVID19-cases.csv")
+# load the first datastore resource as a sample
+data <- filter(datastore_resources, row_number()==1) %>% get_resource()
+write_csv(data, "inputs/data/COVID19-cases.csv")
 

### 2022-02-07 outputs/paper/paper.Rmd
done

@@
 ---
-title: "Who was most affected by COVID-19 in Toronto"
+title: "Who were most affected by COVID-19 in Toronto"
 author: 
   - Lantao Cui
-thanks: "Code and data are available at: https://github.com/cuilantao/STA304-Paper1."
+thanks: "Code and data are available at: https://github.com/cuilantao/Impace-of-COVID19-on-Toronto."
 date: "`r format(Sys.time(), '%d %B %Y')`"
@@
 Ever since the dawn of civilization, humanity had been fighting against different plagues. The earliest recorded pandemic happened during the
-Peloponnesian war, which is almost 3000 years from now. This plague wiped through all of Libya, Ethiopia and Egypt, killed almost two-thirds of 
+Peloponnesian war, which was almost 3000 years from now. This plague wiped through all of Libya, Ethiopia and Egypt, killed almost two-thirds of 
 the entire population.
@@
 But after the industrial revolution, the technology advanced so fast and people developed the illusion that we should be able to defeat any kinds of plague.
-Therefore, nobody cared at all when COVID first started, until it started to take away millions of people's lives.
+Therefore, nobody cared at all when COVID-19 first started, until it started to take away millions of people's lives.
 
@@
 ## Data overview
-This dataset contains all of the demographic, geographic, and severity data of the reported COVID-19 cases in City of Toronto.
+This dataset contains all of the demographic, geographic, and severity data of the reported COVID-19 cases in the City of Toronto.
 It has a total of 272017 cases and has 18 attributes.
-The first two attributes serves as an identical identifier and are removed in the data pre-processing step.
+The first two attributes serves as a distinct identifier and are removed in the data pre-processing step.
 The
@@
 However, this is not always the case, during the 1918 flu, millions of healthy young people died, this is because the 1918 flu triggered a cytokine storm.
-Basically this will turn your own immune system against you, so there are less deaths in older and middle-aged adults because they have a weaker immune system.
-Figure 1 made by ggplot2[@plot], Table 1 made by KableExtra [@kabel] and Knitr [@knitr] shows total number of confirmed COVID-19 cases among each group, and the severity of those COVID-19 cases.
+Basically this will turn your own immune system against you, as a result, there were less deaths in older and middle-aged adults because they have a weaker immune system.
+To see if COVID-19 has a simular effect, Figure 1 made by ggplot2[@plot], Table 1 made by KableExtra [@kabel] and Knitr [@knitr] shows total number of confirmed COVID-19 cases among each age group, and the severity of those COVID-19 cases.
 
@@
 As people's age increase, the mortality and hospitalization rate grow almost exponentially, the mortality rate of kid under 19 years old is 0.00007, but this number increases to 0.23 when the person is older than 90, which is a factor of 3285.
-Study shows that "adults over 65 years of age represent 80% of hospitalizations and have a 23-fold greater risk of death than those under 65" [@mueller].
+Study also shows that "adults over 65 years of age represent 80% of hospitalizations and have a 23-fold greater risk of death than those under 65" [@mueller].
 The reason for this is that as people ages, their immune system function will gradually decline, which makes them more vulnerable to virus.
@@
 The next thing we will explore is the effect of COVID-19 on different communities in Toronto.
-After grouping by and sorting the data using R [@citeR], Figure 2 are produced with ggplot2 [@plot].
-The figure plots the top 10 communities with the most COVID-19 infections, a quick research shows those are mostly low-income communities or neighborhood that has a large population density.
+After grouping by and sorting the data using R [@citeR], Figure 2 is produced with ggplot2 [@plot].
+The figure plots the top 10 communities with the most COVID-19 infections, a quick research shows those are mostly low-income communities or neighborhood that have a large population density.
 This is because most jobs with low income require the worker to have much more in-person interactions with other people, thus increasing the risk of COVID-19 infection.
 And a high density neighborhood usually has a lot of apartment buildings, and it's relatively easier for the virus to spread within an apartment building because people are sharing lots of things such as air vent and elevator.
-This finding shows that COVID-19 situations varies across different communities and it maybe beneficial if the government starts to enforce different procedure based on different communities.
+This finding shows that COVID-19 situations varies across different communities and it maybe beneficial if the government starts to enforce different procedures based on different communities.
 
@@
 ## Conclusion
-Our findings clearly revealed that COVID-19 hits certain people and neighborhood really hard and they require more attention from the government.
+Our findings clearly revealed that COVID-19 hits certain people and neighborhood harder and they require more attention from the government.
 Luckily, the City of Toronto is aware of this situation and have launched support programs

### 2022-02-07 outputs/paper/paper.Rmd
add readme

@@
 ---
-title: "Who were most affected by COVID-19 in Toronto"
+title: "Old people and low-income communities are most affected by COVID-19"
 author: 
   - Lantao Cui
-thanks: "Code and data are available at: https://github.com/cuilantao/Impace-of-COVID19-on-Toronto."
+thanks: "Code and data are available at: https://github.com/cuilantao/Impact-of-COVID19-on-Toronto."
 date: "`r format(Sys.time(), '%d %B %Y')`"

### 2022-02-07 outputs/paper/paper.Rmd
add readme

@@
 ```{r setup, include = FALSE}
+# We load all necessary libraries
 knitr::opts_chunk$set(echo = TRUE)
@@
 library(kableExtra)
-wd <- getwd()
-wd
-setwd("../..")
-covid19_cases_cleaned <- read_csv("inputs/data/COVID19-cases-clean.csv")
+library(here)
+# Read the dataset, use here to navigate to working directory
+covid19_cases_cleaned <- read_csv(here::here("inputs/data/COVID19-cases-clean.csv"))
 head(covid19_cases_cleaned)
@@
 
-To find out who was most affected, we obtained all of COVID-19 case reports from the City of Toronto's data portal.
+To find out who was most affected, we obtained all of COVID-19 case reports from the City of Toronto's data portal [@opendatac].
 After some investigation, we found out that as the patient's age increases, the mortality and hospitalization rate also increases exponentially.
@@
 
-Our findings have lots of implications, it identifies the groups of people and neighborhood that are most affected by COVID-19, this information will allow the government to better support them and come up with new proceudres that will
+This report will first find out if there exists a correlation between age and the mortality rate of COVID-19.
+Then it will attempt to find out which community in Toronto is most affect by COVID-19.
+Our findings have lots of implications, it will help to identify the groups of people and neighborhood that are at high risk, this information will allow the government to better support them and come up with new procedures that will
 slow down the spread of COVID-19.
@@
   summarize(n())
+# Change column name from n() to Total Covid Cases
 names(covid_combined_by_age_group)[names(covid_combined_by_age_group) == 'n()'] <- 'Total Covid Cases'
 
+# Find out all fatal covid cases
 fatal_covid_cases <- covid19_cases_cleaned %>% filter(`Outcome` == 'FATAL')
@@
   summarize(n())
+# Change the name
 names(fatal_covid_case_combined_by_age_group)[names(fatal_covid_case_combined_by_age_group) == 'n()'] <- 'Fatal Cases'
 
+# Combine the two data frame, now for each age group, we know the total covid case and the fatal ones
 total_case_and_fatal_case <- merge(covid_combined_by_age_group,fatal_covid_case_combined_by_age_group,by="Age Group")
@@
   summarize(n())
+
+# Combine the two data frame and calculate the hospitalization rate by using Hospitalized / Total Covid Cases
 names(cases_that_went_to_hospital_combined_by_age_group)[names(cases_that_went_to_hospital_combined_by_age_group) == 'n()'] <- 'Hospitalized'
@@
 ```{r include = FALSE}
+# Construct a new dataframe, it contains identical information, but is easier to plot
 age_group_without_case_count <- subset( total_case_and_fatal_case, select = -c(`Total Covid Cases`, `Fatal Cases` ))
@@
 ```{r, include = FALSE}
+# Group covid case by Neighbourhood Name
 covid_combined_by_postal_code <-
@@
 ```{r, include = FALSE}
+# Sort by case counts, and get the first 10
 total_case_by_postal_sorted <- covid_combined_by_postal_code[order(-covid_combined_by_postal_code$n),]

### 2022-02-07 outputs/paper/paper.Rmd
add readme

@@
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "The first COVID-19 case was reported on 31 December 2019, exactly two years from now.
-At first, everyone thought that this is nothing but a seasonal flu and it will end in less than a month, however, it turned out to be a global pandemic and has taken numerous people's lives.
-In this paper, We obtain and analyze all reported COVID-19 cases in the city of Toronto.
+abstract: "The first COVID-19 case was reported on 31 December 2019, approximately two years from now.
+At first, everyone thought that this was nothing but a seasonal flu which would end in less than a month, however, it turned out to be a global pandemic and has taken numerous people's lives.
+In this paper, we obtain and analyze all reported COVID-19 cases in the city of Toronto.
 We found out that COVID-19 is more fatal toward elders and hits hardest on communities with low income or high population density.
@@
 # Data
-## Data Source
+## Data Source.
 This dataset contains all of the data reported to Toronto Public Health and are gathered through an R package called "opendatatoronto" [@opendatator].

### 2022-02-07 outputs/paper/paper.Rmd
add readme

@@
 Another well known plague is the black death, which lasted for decades and was responsible for the death of nearly one-thirds of the World Population.
-But after the industrial revolution, the technology advanced so fast and people developed the illusion that we should be able to defeat any kinds of plague.
+But after the industrial revolution, technology advanced so fast and people developed the illusion that we should be able to defeat any kinds of plague.
 Therefore, nobody cared at all when COVID-19 first started, until it started to take away millions of people's lives.
@@
 The mortality rate of kids under 19 years old is 0.00007 and this number increases to 0.23 for people above 90 years old, by a factor of 3000.
-On top of that, low income or high density neighbourhood are hit the hardest during this pandemic.
+On top of that, low-income or high-density neighborhood are hit the hardest during this pandemic.
 Among 140 different communities, the top 10 communities with the most COVID-19 cases have contributed 20% of Toronto's total COVID-19 cases.
@@
 This report will first find out if there exists a correlation between age and the mortality rate of COVID-19.
-Then it will attempt to find out which community in Toronto is most affect by COVID-19.
-Our findings have lots of implications, it will help to identify the groups of people and neighborhood that are at high risk, this information will allow the government to better support them and come up with new procedures that will
+Then it will attempt to find out which community in Toronto is most affected by COVID-19.
+Our findings have lots of implications, it will help to identify the groups of people and neighborhoods that are at high risk, this information will allow the government to better support them and come up with new procedures that will
 slow down the spread of COVID-19.
@@
 ## Data Source.
-This dataset contains all of the data reported to Toronto Public Health and are gathered through an R package called "opendatatoronto" [@opendatator].
+This dataset contains all of the data reported to Toronto Public Health and is gathered through an R package called "opendatatoronto" [@opendatator].
 This dataset contains all of the demographic, geographic, and severity information for all of the confirmed and potential cases of COVID-19.
@@
 The strength of this dataset is that it is very detailed and contains a lot of valuable information, for instance, for every reported case, this dataset will track it and include the final result.
-This can help us to analyze the mortality rate of COVID-19 on different age groups.
+This can help us to analyze the mortality rate of COVID-19 in different age groups.
 However, although the dataset contains all of the reported cases, it can not be viewed as
@@
 It has a total of 272017 cases and has 18 attributes.
-The first two attributes serves as a distinct identifier and are removed in the data pre-processing step.
+The first two attributes serve as a distinct identifier and are removed in the data pre-processing step.
 The
 next 5 attributes contain information about the age of the patient, their source of infection and the neighborhood they live in.
-The next 5 columns are about the gender of the patient, whether case is probable or confirmed, and the outcome.
+The next 5 columns are about the gender of the patient, whether the case is probable or confirmed, and the outcome.
 The final 6 columns help to assess the severity of the case.
@@
 ## The effect of COVID-19 on different age groups
-People always have the illusion that younger people are less affected from disease because they have a stronger immune system.
+People always have the illusion that younger people are less affected by disease because they have a stronger immune system.
 However, this is not always the case, during the 1918 flu, millions of healthy young people died, this is because the 1918 flu triggered a cytokine storm.
-Basically this will turn your own immune system against you, as a result, there were less deaths in older and middle-aged adults because they have a weaker immune system.
-To see if COVID-19 has a simular effect, Figure 1 made by ggplot2[@plot], Table 1 made by KableExtra [@kabel] and Knitr [@knitr] shows total number of confirmed COVID-19 cases among each age group, and the severity of those COVID-19 cases.
+Basically, this will turn your own immune system against you, as a result, there were fewer deaths in older and middle-aged adults because they have a weaker immune system.
+To see if COVID-19 has a similar effect, Figure 1 made by ggplot2[@plot], Table 1 made by KableExtra [@kabel] and Knitr [@knitr] shows the total number of confirmed COVID-19 cases among each age group, and the severity of those COVID-19 cases.
 
@@
 Study also shows that "adults over 65 years of age represent 80% of hospitalizations and have a 23-fold greater risk of death than those under 65" [@mueller].
-The reason for this is that as people ages, their immune system function will gradually decline, which makes them more vulnerable to virus.
+The reason for this is that as people age, their immune system function will gradually decline, which makes them more vulnerable to virus.
 Another reason is that older people are more likely to have underlying health conditions such as diabetes and high blood pressure.
-Those health condition will worsen the symptom of COVID-19 and make it more fatal.
+Those health conditions will worsen the symptom of COVID-19 and make it more fatal.
 
@@
 After grouping by and sorting the data using R [@citeR], Figure 2 is produced with ggplot2 [@plot].
-The figure plots the top 10 communities with the most COVID-19 infections, a quick research shows those are mostly low-income communities or neighborhood that have a large population density.
+The figure plots the top 10 communities with the most COVID-19 infections, a quick research shows those are mostly low-income communities or neighborhoods that have a large population density.
 This is because most jobs with low income require the worker to have much more in-person interactions with other people, thus increasing the risk of COVID-19 infection.
-And a high density neighborhood usually has a lot of apartment buildings, and it's relatively easier for the virus to spread within an apartment building because people are sharing lots of things such as air vent and elevator.
-This finding shows that COVID-19 situations varies across different communities and it maybe beneficial if the government starts to enforce different procedures based on different communities.
+And a high-density neighborhood usually has a lot of apartment buildings, and it's relatively easier for the virus to spread within an apartment building because people are sharing lots of things such as air vents and elevators.
+This finding shows that COVID-19 situations vary across different communities and it maybe beneficial if the government starts to enforce different procedures based on different communities.
 
@@
 ## Conclusion
-Our findings clearly revealed that COVID-19 hits certain people and neighborhood harder and they require more attention from the government.
+Our findings clearly revealed that COVID-19 hits certain people and neighborhoods harder and they require more attention from the government.
 Luckily, the City of Toronto is aware of this situation and have launched support programs
-targeting those neighborhood.
-For instance, the City of Toronto is offering free self-isolation sites for those people diagnosed with COVID-19 and is also giving seniors and people with underlying health condition top priority in the vaccination program.
+targeting those neighborhoods.
+For instance, the City of Toronto is offering free self-isolation sites for those people diagnosed with COVID-19 and is also giving seniors and people with underlying health conditions top priority in the vaccination program.
 

### 2022-02-07 outputs/paper/paper.Rmd
add readme

@@
 
-## Conclusion
+# Conclusion
 Our findings clearly revealed that COVID-19 hits certain people and neighborhoods harder and they require more attention from the government.

### 2022-04-04 scripts/01-data_download.R
change

@@ -1,28 +1,0 @@
-#### Preamble ####
-# Purpose: Download data from opendatatoronto 
-# Author: Lantao Cui
-# Data: 31 January 2021
-# Contact: lantao.cui@mail.utoronto.ca
-# License: MIT
-
-
-## Opendata toronto's get_resource function sometimes doesnt work and return code 500. If this happens, please go to https://open.toronto.ca/dataset/covid-19-cases-in-toronto/ and manually download the data,
-## then put it inside inputs/data/COVID19-cases.csv. Thank you!
-#### Workspace setup ####
-library(opendatatoronto)
-library(dplyr)
-
-# get package
-package <- show_package("64b54586-6180-4485-83eb-81e8fae3b8fe")
-package
-
-# get all resources for this package
-resources <- list_package_resources("64b54586-6180-4485-83eb-81e8fae3b8fe")
-
-# identify datastore resources; by default, Toronto Open Data sets datastore resource format to CSV for non-geospatial and GeoJSON for geospatial resources
-datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))
-
-# load the first datastore resource as a sample
-data <- filter(datastore_resources, row_number()==1) %>% get_resource()
-write_csv(data, "inputs/data/COVID19-cases.csv")
-

### 2022-04-04 scripts/02-data_preprocessing.R

@@ -1,31 +1,0 @@
-#### Preamble ####
-# Purpose: Preprocess the data for future analyze
-# Author: Lantao Cui
-# Data: 31 January 2021
-# Contact: lantao.cui@mail.utoronto.ca
-# License: MIT
-
-#### load the libraies we need ####
-library(tidyverse)
-library(dplyr)
-
-#### Read the csv files ####
-city_of_toronto_covid_cases <- read_csv("inputs/data/COVID19-cases.csv")
-
-
-#### Remove the ID column, we don't need them for the analyze ####
-city_of_toronto_covid_cases_clean <- city_of_toronto_covid_cases[-c(1,2)]
-
-#### Let's find out if there are any NAs in this dataset ####
-number_of_nas <- sum(is.na(city_of_toronto_covid_cases_clean))
-
-
-#### We found out that there are NA values, so we should remove them as they will affect the data analyze ####
-covid_case_with_na_remove <- na.omit(city_of_toronto_covid_cases_clean)
-
-#### Double check that there is no more NA values ####
-stopifnot(sum(is.na(covid_case_with_na_remove)) == 0)
-
-#### Now we can save the cleaned data ####
-write_csv(covid_case_with_na_remove,"inputs/data/COVID19-cases-clean.csv")
-

### 2022-04-07 outputs/paper/paper.Rmd
initial submission

--- 2022-02-07 outputs/paper/paper.Rmd
@@
 ---
-title: "Old people and low-income communities are most affected by COVID-19"
+title: "Toronto's Reaction to Fight Against Global Warming"
 author: 
   - Lantao Cui
-thanks: "Code and data are available at: https://github.com/cuilantao/Impact-of-COVID19-on-Toronto."
+thanks: "Code and data are available at: https://github.com/cuilantao/Toronto-s-reaction-to-fight-against-global-warming"
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "The first COVID-19 case was reported on 31 December 2019, approximately two years from now.
-At first, everyone thought that this was nothing but a seasonal flu which would end in less than a month, however, it turned out to be a global pandemic and has taken numerous people's lives.
-In this paper, we obtain and analyze all reported COVID-19 cases in the city of Toronto.
-We found out that COVID-19 is more fatal toward elders and hits hardest on communities with low income or high population density.
-Our findings will help the city of Toronto to better help those people at needs."
+abstract: "Climate change and global warming are predominant problems nowadays, in the north pole, polar ice caps are melting at a rate of almost 14% per decade.
+On top of that, over the past 30 years, the oldest and thickest ice in the north pole has declined by almost 95%.
+The majority of the Science Community believes that global warming is caused by the excessive emission of greenhouse gases such as Carbon Dioxide and Methane.
+Luckily, a lot of countries are actively trying to limit the emission of such gases to fight against climate change.
+In this paper, we will obtain and analyze different Toronto organizations' Energy consumption and Green House Gas emissions from 2011 to 2017.
+Our findings can help the city government to establish better climate strategies."
 output:
@@
 
-```{r setup, include = FALSE}
-# We load all necessary libraries
-knitr::opts_chunk$set(echo = TRUE)
+# Introduction
 
-library(tidyverse)
-library(palmerpenguins)
-library(kableExtra)
-library(here)
-# Read the dataset, use here to navigate to working directory
-covid19_cases_cleaned <- read_csv(here::here("inputs/data/COVID19-cases-clean.csv"))
-head(covid19_cases_cleaned)
-```
-
-# Introduction
-Ever since the dawn of civilization, humanity had been fighting against different plagues. The earliest recorded pandemic happened during the
-Peloponnesian war, which was almost 3000 years from now. This plague wiped through all of Libya, Ethiopia and Egypt, killed almost two-thirds of 
-the entire population.
-Another well known plague is the black death, which lasted for decades and was responsible for the death of nearly one-thirds of the World Population.
-But after the industrial revolution, the technology advanced so fast and people developed the illusion that we should be able to defeat any kinds of plague.
-Therefore, nobody cared at all when COVID-19 first started, until it started to take away millions of people's lives.
-
-To find out who was most affected, we obtained all of COVID-19 case reports from the City of Toronto's data portal [@opendatac].
-After some investigation, we found out that as the patient's age increases, the mortality and hospitalization rate also increases exponentially.
-The mortality rate of kids under 19 years old is 0.00007 and this number increases to 0.23 for people above 90 years old, by a factor of 3000.
-On top of that, low income or high density neighbourhood are hit the hardest during this pandemic.
-Among 140 different communities, the top 10 communities with the most COVID-19 cases have contributed 20% of Toronto's total COVID-19 cases.
-
-This report will first find out if there exists a correlation between age and the mortality rate of COVID-19.
-Then it will attempt to find out which community in Toronto is most affect by COVID-19.
-Our findings have lots of implications, it will help to identify the groups of people and neighborhood that are at high risk, this information will allow the government to better support them and come up with new procedures that will
-slow down the spread of COVID-19.
+Ever since Industrial Revolution, people's life has become more and more convenient, for example, the invention of the steam engine made transportation much more easier.
+However, this convenience comes with great drawbacks, over the entire industrial revolution, scientist estimated that a total of 2.3 trillion tonnes of Carbon Dioxide have been released into the atmosphere, what is even worse is that those Carbon Dioxide has a life span of 300 - 1000 years, this means that those climate change can happen on the time scale of many generations' lives.
+The reason those green house gases cause global warming is because they will reflect the heat radiated from Earths' surface back, thus making the Earth warmer.
+However, hundreds of nations are actively trying to fight against Climate Change, some are planting more trees so that the excessive Carbon Dioxide can be absorbed through Photosynthesis, some are developing more sustainable and environment-free energy source such as solar power.
+In this paper, we will obtain and analyze different Toronto organizations' Energy consumption and Green House Gas emissions from 2011 to 2017, we aim to find out Toronto's contribution in limiting the emission of green house gases.
 
 # Data
-## Data Source.
-This dataset contains all of the data reported to Toronto Public Health and are gathered through an R package called "opendatatoronto" [@opendatator].
-This dataset contains all of the demographic, geographic, and severity information for all of the confirmed and potential cases of COVID-19.
-It's updated on a weekly basis and was last updated on Feb 2, 2022.
 
-## Data Collection and Methodology
-All of COVID-19 cases are reported to Toronto Public Health by local testing laboratories, then Open data toronto collect those data from the provincial Case & Contact Management System.
-The strength of this dataset is that it is very detailed and contains a lot of valuable information, for instance, for every reported case, this dataset will track it and include the final result.
-This can help us to analyze the mortality rate of COVID-19 on different age groups.
-However, although the dataset contains all of the reported cases, it can not be viewed as
-an accurate measure of the actual COVID-19 cases because of various reasons.
-The most notable problem is that you have to get tested to be officially diagnosed with COVID-19.
-This leads to several problems, first of all, COVID-19 has similar symptoms as a seasonal flu or a common cold, so some people will refuse to get tested.
-Another problem is the shortage of testing kits, according to the Ontario Government, due to the fast spread of the Omicron variant, PCR tests are only available to "high-risk individuals and individuals who work at high-risk settings".
-Therefore, those numbers should only be interpreted as "an underestimate of the true number of individuals with COVID-19 in Toronto".
+## Data Source
 
-## Data overview
-This dataset contains all of the demographic, geographic, and severity data of the reported COVID-19 cases in the City of Toronto.
-It has a total of 272017 cases and has 18 attributes.
-The first two attributes serves as a distinct identifier and are removed in the data pre-processing step.
-The
-next 5 attributes contain information about the age of the patient, their source of infection and the neighborhood they live in.
-The next 5 columns are about the gender of the patient, whether case is probable or confirmed, and the outcome.
-The final 6 columns help to assess the severity of the case.
-To get a better understanding of the actual data, let us take a look at Figure 1, which is a sample view of the data and is produced by R [@citeR];
+## Methodology and Data Collection
 
-```{r echo=FALSE}
-head(covid19_cases_cleaned)
-```
-## The effect of COVID-19 on different age groups
-People always have the illusion that younger people are less affected from disease because they have a stronger immune system.
-However, this is not always the case, during the 1918 flu, millions of healthy young people died, this is because the 1918 flu triggered a cytokine storm.
-Basically this will turn your own immune system against you, as a result, there were less deaths in older and middle-aged adults because they have a weaker immune system.
-To see if COVID-19 has a simular effect, Figure 1 made by ggplot2[@plot], Table 1 made by KableExtra [@kabel] and Knitr [@knitr] shows total number of confirmed COVID-19 cases among each age group, and the severity of those COVID-19 cases.
+# Results
 
-```{r,include = FALSE}
-# first find out which age group has the most reported covid 19 cases
-covid_combined_by_age_group <-
-  group_by(covid19_cases_cleaned, `Age Group`) %>%
-  summarize(n())
-# Change column name from n() to Total Covid Cases
-names(covid_combined_by_age_group)[names(covid_combined_by_age_group) == 'n()'] <- 'Total Covid Cases'
-
-# Find out all fatal covid cases
-fatal_covid_cases <- covid19_cases_cleaned %>% filter(`Outcome` == 'FATAL')
-fatal_covid_case_combined_by_age_group <- fatal_covid_cases %>% 
-  group_by(`Age Group`) %>% 
-  summarize(n())
-# Change the name
-names(fatal_covid_case_combined_by_age_group)[names(fatal_covid_case_combined_by_age_group) == 'n()'] <- 'Fatal Cases'
-
-# Combine the two data frame, now for each age group, we know the total covid case and the fatal ones
-total_case_and_fatal_case <- merge(covid_combined_by_age_group,fatal_covid_case_combined_by_age_group,by="Age Group")
-total_case_and_fatal_case$Mortality_Rate <- with(total_case_and_fatal_case, round(`Fatal Cases` / `Total Covid Cases`, 5))
-
-# ICU cases
-cases_that_went_to_hospital <- covid19_cases_cleaned %>% filter(`Ever Hospitalized` == 'Yes');
-cases_that_went_to_hospital_combined_by_age_group <- cases_that_went_to_hospital %>% 
-  group_by(`Age Group`) %>%
-  summarize(n())
-
-# Combine the two data frame and calculate the hospitalization rate by using Hospitalized / Total Covid Cases
-names(cases_that_went_to_hospital_combined_by_age_group)[names(cases_that_went_to_hospital_combined_by_age_group) == 'n()'] <- 'Hospitalized'
-total_case_fatal_hos <- merge(total_case_and_fatal_case, cases_that_went_to_hospital_combined_by_age_group, by = "Age Group")
-total_case_fatal_hos$Hospital_Rate <- with(total_case_fatal_hos, round(`Hospitalized` / `Total Covid Cases`, 5))
-total_case_fatal_hos
-```
-
-```{r , fig.cap="Effect of COVID-19 on different Age Group", echo=FALSE, warning=FALSE, message = FALSE}
-total_case_fatal_hos %>%
-  knitr::kable(caption = "Effect of COVID-19 on different Age Group", 
-               col.names = c("Age Group", "Total COVID-19 Cases", "Fatal Cases", "Mortality Rate", "Hospitalized", "Hospitalized Rate"),
-               align = c('l', 'l', 'l', 'l', 'l', 'l'),
-               booktabs = T) %>%
-  kable_styling(full_width = T, latex_options = "hold_position")
-```
-
-```{r include = FALSE}
-# Construct a new dataframe, it contains identical information, but is easier to plot
-age_group_without_case_count <- subset( total_case_and_fatal_case, select = -c(`Total Covid Cases`, `Fatal Cases` ))
-age_group_without_case_count$Type <- "Mortality Rate"
-names(age_group_without_case_count)[names(age_group_without_case_count) == 'Mortality_Rate'] <- 'Rate'
-another_frame <- subset(total_case_fatal_hos, select = -c(`Total Covid Cases`, `Fatal Cases`, `Hospitalized`, `Mortality_Rate`))
-names(another_frame)[names(another_frame) == 'Hospital_Rate'] <- 'Rate'
-another_frame$Type <- "Hospitalized Rate"
-new <- rbind(age_group_without_case_count, another_frame)
-new$`Age Group`[new$`Age Group`=="19 and younger"] <- "19 and younger"
-new$`Age Group`[new$`Age Group`=="20 to 29 Years"] <- "20-29"
-new$`Age Group`[new$`Age Group`=="30 to 39 Years"] <- "30-39"
-new$`Age Group`[new$`Age Group`=="40 to 49 Years"] <- "40-49"
-new$`Age Group`[new$`Age Group`=="50 to 59 Years"] <- "50-59"
-new$`Age Group`[new$`Age Group`=="60 to 69 Years"] <- "60-69"
-new$`Age Group`[new$`Age Group`=="70 to 79 Years"] <- "70-79"
-new$`Age Group`[new$`Age Group`=="80 to 89 Years"] <- "80-89"
-new$`Age Group`[new$`Age Group`=="90 and older"] <- "Above 90"
-```
-
-```{r, fig.cap="Effect of COVID-19 on different Age Groups", echo=FALSE, warning=FALSE, message = FALSE, fig.width=8, fig.height=3}
-ggplot(new, aes(x=`Age Group`, y=`Rate`,group = `Type`, color = `Type`)) +
-    geom_line()
-```
-
-From the figure and table, it's clear that there is some correlation between people's age and the effect of COVID-19.
-As people's age increase, the mortality and hospitalization rate grow almost exponentially, the mortality rate of kid under 19 years old is 0.00007, but this number increases to 0.23 when the person is older than 90, which is a factor of 3285.
-Study also shows that "adults over 65 years of age represent 80% of hospitalizations and have a 23-fold greater risk of death than those under 65" [@mueller].
-The reason for this is that as people ages, their immune system function will gradually decline, which makes them more vulnerable to virus.
-Another reason is that older people are more likely to have underlying health conditions such as diabetes and high blood pressure.
-Those health condition will worsen the symptom of COVID-19 and make it more fatal.
-
-## The effect of COVID-19 on different communities in Toronto
-The next thing we will explore is the effect of COVID-19 on different communities in Toronto.
-After grouping by and sorting the data using R [@citeR], Figure 2 is produced with ggplot2 [@plot].
-The figure plots the top 10 communities with the most COVID-19 infections, a quick research shows those are mostly low-income communities or neighborhood that have a large population density.
-This is because most jobs with low income require the worker to have much more in-person interactions with other people, thus increasing the risk of COVID-19 infection.
-And a high density neighborhood usually has a lot of apartment buildings, and it's relatively easier for the virus to spread within an apartment building because people are sharing lots of things such as air vent and elevator.
-This finding shows that COVID-19 situations varies across different communities and it maybe beneficial if the government starts to enforce different procedures based on different communities.
-
-```{r, include = FALSE}
-# Group covid case by Neighbourhood Name
-covid_combined_by_postal_code <-
-  group_by(covid19_cases_cleaned, `Neighbourhood Name`) %>%
-  summarize(n())
-names(covid_combined_by_postal_code)[names(covid_combined_by_postal_code) == 'n()'] <- 'n'
-```
-
-```{r, include = FALSE}
-# Sort by case counts, and get the first 10
-total_case_by_postal_sorted <- covid_combined_by_postal_code[order(-covid_combined_by_postal_code$n),]
-total_case_by_postal_sorted
-top_10 <- total_case_by_postal_sorted[1:10, ]
-top_10
-```
-
-\pagebreak
-```{r, fig.cap="Effect of COVID-19 on different communities", echo=FALSE, warning=FALSE, message = FALSE, fig.width=10, fig.height=4}
-ggplot(data=top_10, aes(x = reorder(`Neighbourhood Name`, n), y=n)) +
-  geom_bar(stat="identity", position=position_dodge()) + coord_flip()
-```
-
-## Conclusion
-Our findings clearly revealed that COVID-19 hits certain people and neighborhood harder and they require more attention from the government.
-Luckily, the City of Toronto is aware of this situation and have launched support programs
-targeting those neighborhood.
-For instance, the City of Toronto is offering free self-isolation sites for those people diagnosed with COVID-19 and is also giving seniors and people with underlying health condition top priority in the vaccination program.
-
-\pagebreak
-
-# References
+# Discussion

### 2022-04-22 outputs/paper/paper.Rmd
finished investigating on the effects of income and age on concern about climate change, will then look at education and gender and finish the paper

@@
 The majority of the Science Community believes that global warming is caused by the excessive emission of greenhouse gases such as Carbon Dioxide and Methane.
-Luckily, a lot of countries are actively trying to limit the emission of such gases to fight against climate change.
-In this paper, we will obtain and analyze different Toronto organizations' Energy consumption and Green House Gas emissions from 2011 to 2017.
-Our findings can help the city government to establish better climate strategies."
+Luckily, people are getting more and more aware of the global change and are willing to make changes.
+In this paper, we obtain a survey conducted on Toronto's residents about their perceptions of climate change and their willingness to take action on it.
+We aim to find out the impact of demographic factors such as personal income on people's perception of climate change."
 output:
@@
 
+```{r setup, include = FALSE}
+# Import all necessary libraries
+knitr::opts_chunk$set(echo = TRUE)
+library(tidyverse)
+library(palmerpenguins)
+library(kableExtra)
+library(here)
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(readxl)
+library(plotrix)
+# Read the dataset, use here to navigate to working directory
+global_avg_temperature <- read_csv(here::here("inputs/data/GlobalTemperatures.csv"))
+
+#annual_energy_2011 <- read_csv(here::here("inputs/data/energy-2011.csv"))
+#annual_energy_2012 <- read_csv(here::here("inputs/data/energy-2012.csv"))
+#annual_energy_2013 <- read_csv(here::here("inputs/data/energy-2013.csv"))
+#annual_energy_2014 <- read_csv(here::here("inputs/data/energy-2014.csv"))
+#annual_energy_2015 <- read_csv(here::here("inputs/data/energy-2015.csv"))
+#annual_energy_2016 <- read_csv(here::here("inputs/data/energy-2016.csv"))
+#annual_energy_2017 <- read_csv(here::here("inputs/data/energy-2017.csv"))
+#annual_energy_2018 <- read_csv(here::here("inputs/data/energy-2018.csv"))
+climate_perception <- read_csv(here::here("inputs/data/survey.csv"))
+```
+
 # Introduction
@@
 The reason those green house gases cause global warming is because they will reflect the heat radiated from Earths' surface back, thus making the Earth warmer.
-However, hundreds of nations are actively trying to fight against Climate Change, some are planting more trees so that the excessive Carbon Dioxide can be absorbed through Photosynthesis, some are developing more sustainable and environment-free energy source such as solar power.
-In this paper, we will obtain and analyze different Toronto organizations' Energy consumption and Green House Gas emissions from 2011 to 2017, we aim to find out Toronto's contribution in limiting the emission of green house gases.
+Figure \@ref(fig:land-average-temperature) shows the average land temperature on Earth in the past 100 years, Figure \@ref(fig:ocean-average-temperature) shows the average Ocean temperature on Earth in the past 100 years, the data are obtained from Berkeley Earth Data Portal [@berkeleyearth].
+
+```{r land-average-temperature, fig.cap='Land Average Temperature', echo=FALSE, warning=FALSE, message = FALSE, fig.width=5, fig.height=3, fig.pos = "!H"}
+# Part of the below code are from https://www.kaggle.com/code/jagelves/continental-us-climate-change-1850-2013/report?scriptVersionId=0
+cleaned_avg_temp <- global_avg_temperature %>%
+  separate(col = dt, into = c("Year", "Month", "Day"), convert = TRUE)
+cleaned_avg_temp <- na.omit(cleaned_avg_temp)
+
+Land_Avg_sum <- cleaned_avg_temp %>% 
+  filter(Year>1850) %>%
+  group_by(Year) %>% 
+  summarise(AverageTemperature = mean(LandAverageTemperature))
+
+qplot(Year, AverageTemperature, data=Land_Avg_sum, main="Land Average Temperature 1850-2013",geom=c("point","smooth"))+ aes(colour = AverageTemperature) + scale_color_gradient(low="blue", high="red")
+
+```
+
+```{r ocean-average-temperature, fig.cap='Ocean Average Temperature', echo=FALSE, warning=FALSE, message = FALSE, fig.width=5, fig.height=3, fig.pos = "!H"}
+# Part of the below code are from https://www.kaggle.com/code/jagelves/continental-us-climate-change-1850-2013/report?scriptVersionId=0
+cleaned_avg_temp <- global_avg_temperature %>%
+  separate(col = dt, into = c("Year", "Month", "Day"), convert = TRUE)
+cleaned_avg_temp <- na.omit(cleaned_avg_temp)
+
+Land_Avg_sum <- cleaned_avg_temp %>% 
+  filter(Year>1850) %>%
+  group_by(Year) %>% 
+  summarise(AverageTemperature = mean(LandAverageTemperature))
+
+qplot(Year, AverageTemperature, data=Land_Avg_sum, main="Ocean Average Temperature 1850-2013",geom=c("point","smooth"))+ aes(colour = AverageTemperature) + scale_color_gradient(low="blue", high="red")
+
+```
+
+From the above two figures, it is very clear that the Earth's temperature is increasing rapidly after the Industrial Revolution.
+Based on research, Earth's temperature has risen by 0.08 Celsius per decade since 1880, and the rate of warming over the past 40 years is more than twice of that, 0.18 Celsius per decade.
+People might develop the illusion that because this looks like a very small increase, it will have little or no impact on Earth's environment.
+However, this is wrong, the total volume of the Ocean on Earth is around 1.335 billion cubic kilometers, therefore, a tremendous amount of energy is required to heat up the ocean [@dahlman].
+
+Global warming has been regarded as a high-risk problem globally because it will trigger a chain of events.
+For instance, the increased temperature will melt polar ice caps, then those ice water will be released into the ocean, causing the global sea level to rise.
+This could trigger a series of events, for example, the salinity of the ocean will decrease because of this large amount of fresh water, and the decreased salinity is deleterious for certain species such as coral reef, which is a keystone species, meaning its extinction is disastrous to the entire ecosystem.
+Moreover, the melting of the polar ice cap will reveal the black soil under it, those black soil will then absorb more energy from the sun, thus exacerbating global warming.
+
+Luckily, hundreds of nations are actively trying to fight Climate Change, some are planting more trees so that the excessive Carbon Dioxide can be absorbed through Photosynthesis, and some are developing more sustainable and environment-free energy sources such as solar power.
+Toronto, for example, proposed an ambitious plan called TransformTO, its goal is to achieve net-zero greenhouse gas emissions.
+However, everyone has a different level of education, hence it is common for people to hold different opinions about climate change.
+It is reasonable to believe that a university student majoring in environmental science will be more concerned about global warming than someone with high school education.
+To find out if there is a relationship between people's perception of climate change and their demographic factors such as income, level of education, and age, we obtained a city-wide climate perception survey dataset from the City of Toronto Data Portal [@opendatator].
+On top of that, the report written by the City of Toronto was also helpful [@report].
 
 # Data
+We started our data analysis by using R [@citeR], dplyr[@dplyr], tidyverse[@tidyverse], here[@here]. Graphs are generated using ggplot2[@ggplot2], kableExtra[@kableExtra], and gridExtra[@gridExtra].
 
-## Data Source
+## Data Source and Collection
+The dataset I will be using are from the City of Toronto Data Portal, it is conducted city-wide to gather people's opinion on climate change [@opendatator], the goal of this survey is to capture their perceptions about climate change and to estimate people's willingness to take actions and help the city government to establish the goal of achieving net-zero carbon dioxide emission.
+The survey is conducted online and a total of 404 results were received between October 11 to October 18, 2018.
+All survey respondents are adult residents living in the City of Toronto.
+All respondents are from 4 geological areas: Etobicoke-York, North York, Scarborough, and Toronto and East York, Figure \@ref(fig:respondents-number) is a bar graph showing the number of respondents from each area.
 
-## Methodology and Data Collection
+```{r respondents-number, fig.cap='Number of Respondents from Each Area', echo=FALSE, warning=FALSE, message = FALSE, fig.width=5, fig.height=3, fig.pos = "!H"}
+number_from_each_area <- c(99, 101, 91, 113)
+area_name <- c("Etobicoke-York", "North York", "Scarborough", "Toronto and East York")
+ggplot() + geom_bar(aes(x=area_name,y=number_from_each_area), stat='identity') + xlab('Area') + ylab('Number of Respondents')
+```
+
+Other than coming from different city areas, respondents also have different demographic backgrounds, For instance, some respondents have a household income of more than $150000 while some respondents only have a household income lower than $40000.
+The respondents also have a big age variety with some people being 65 years old and some only 20 years old.
+Below are some figures showing the distribution of the respondents based on their demographic factors.
+Figure \@ref(fig:agesum) shows the distributions of respondents based on their age, Figure \@ref(fig:incomesum) shows the distribution of respondents based on their household income.
+Finally, Figure \@ref(fig:edulevel) shows the distribution of respondents based on their level of education.
+
+```{r agesum, fig.cap='Number of Respondents Based on Age', echo=FALSE, warning=FALSE, message = FALSE, fig.width=5, fig.height=3, fig.pos = "!H"}
+
+# Below we will find the age distribution of all the respondents
+
+age_of_all_respondents <- climate_perception %>% filter(`HIDAGE1` != 'NA');
+age_of_all_respondents <- age_of_all_respondents["HIDAGE1"]
+age_group <- age_of_all_respondents %>% mutate(cuts = cut(HIDAGE1, c(17, 25, 40, 55, 65, 150))) %>% 
+  group_by(cuts) %>% 
+  summarize(n=n())
+
+levels(age_group$cuts) <- c("18 to 25", "25 to 40", "40 to 55", "55 to 65", "65+")
+
+ggplot(data=age_group, aes(x = reorder(`cuts`, n), y=n)) +
+  geom_bar(stat="identity", position=position_dodge()) + coord_flip() + xlab('Area') + ylab('Age Range')
+
+```
+
+```{r incomesum, fig.cap='Number of Respondents Based on Household Income', echo=FALSE, warning=FALSE, message = FALSE, fig.width=5, fig.height=3, fig.pos = "!H"}
+
+# Below we will find the income distribution of all the respondents
+
+income_of_all_respondents <- climate_perception %>% filter(`QD6` != 'Prefer not to answer');
+income_of_all_respondents <- income_of_all_respondents["QD6"]
+
+respondents_grouped_by_income <-
+  group_by(income_of_all_respondents, `QD6`) %>%
+  summarize(n())
+
+names(respondents_grouped_by_income)[names(respondents_grouped_by_income) == 'n()'] <- 'n'
+
+ggplot(data=respondents_grouped_by_income, aes(x = reorder(`QD6`, n), y=n)) +
+  geom_bar(stat="identity", position=position_dodge()) + coord_flip() + xlab('Household Income') + ylab('Number of Respondents')
+```
+
+```{r edulevel, fig.cap='Number of Respondents Based on level of education', echo=FALSE, warning=FALSE, message = FALSE, fig.width=5, fig.height=4, fig.pos = "!H"}
+
+# Below we will find the education distribution of all the respondents
+
+education_of_all_respondents <- climate_perception["QD5"]
+
+respondents_grouped_by_education <-
+  group_by(education_of_all_respondents, `QD5`) %>%
+  summarize(n())
+
+names(respondents_grouped_by_education)[names(respondents_grouped_by_education) == 'n()'] <- 'n'
+names(respondents_grouped_by_education)[names(respondents_grouped_by_education) == 'QD5'] <- 'Education Level'
+
+ggplot(data=respondents_grouped_by_education, aes(x ='', y=n, fill = `Education Level`))  + geom_bar(stat = "Identity", width = 4, color = "Yellow") + coord_polar("y", start = 0) + theme_void()
+```
+
+## Relationship between People's Awareness of Climate Change and Various Demographic Factors
+
+Our ultimate goal is to develop a statistical model which takes a person's demographic factor as input, and try to predict whether that person will be concerned about global climate change.
+To do this, we will first take a look at different demographic factors, and determine whether it is relevant.
+
+### Age
+
+Although it is a consensus that global climate change is a problem that needs to be addressed, people from different age groups might view it differently.
+Based on research conducted by the Pew Research Center [@ageper], scientists found out that Gen Z (Born after 1996) and Millennials (Born between 1981 and 1996) are usually more concerned about global climate change than the older generations.
+There are several reasons for this, for example, these generations generally have more access to the internet, which means they are seeing a lot of climate change content online.
+
+We will now take a look at our survey results and determine whether age is a relevant factor.
+The second question in the survey is "For each of the following, how concerned are you about climate change?", the respondents can choose one from the following: "Extremely concerned, Very concerned, Not very concerned, Not at all concerned, Don’t know".
+For simplicity, we will group *Extremely concerned* and *Very concerned* into a big category called *Concerned*, and we will group *Not very concerned* and *Not at all concerned* into a big category called *Not Concerned*, we will neglect *Don't know* answers.
+Figure \@ref(fig:ageconcern) is a summary table.
+
+```{r ageconcern, fig.cap='Concern about Climate Change Based on Age Group', echo=FALSE, warning=FALSE, message = FALSE, fig.width=5, fig.height=4, fig.pos = "!H"}
+age_relevant_data <- subset(climate_perception, select = c(`HIDAGE1`, `Q1r1`))
+names(age_relevant_data)[names(age_relevant_data) == 'HIDAGE1'] <- 'Age'
+names(age_relevant_data)[names(age_relevant_data) == 'Q1r1'] <- 'Concern'
+
+age_relevant_data <- age_relevant_data %>% filter(!str_detect(Concern, "D"))
+
+age_relevant_data$`Concern`[age_relevant_data$`Concern`=="Extremely concerned"] <- "Concerned"
+age_relevant_data$`Concern`[age_relevant_data$`Concern`=="Very concerned"] <- "Concerned"
+
+age_relevant_data$`Concern`[age_relevant_data$`Concern`=="Not very concerned"] <- "Not Concerned"
+age_relevant_data$`Concern`[age_relevant_data$`Concern`=="Not at all concerned"] <- "Not Concerned"
+
+final_age_relevant_data <- age_relevant_data %>% mutate(cuts = cut(Age, c(17, 25, 40, 55, 65, 150))) %>% group_by(cuts, Concern) %>% 
+  summarize(n=n())
+
+final_age_relevant_data <- group_by(final_age_relevant_data, cuts) %>% transmute(Concern, percent = round(n/sum(n),2 ))
+
+levels(final_age_relevant_data$cuts) <- c("18 to 25", "25 to 40", "40 to 55", "55 to 65", "65+")
+
+final_age_relevant_data %>%
+  knitr::kable(caption = "Concern about Climate Change Based on Age Group",
+               col.names = c("Age Group", "Cocern Level", "Percentage WRT Age Group"),
+               align = c('l', 'l', 'l'),
+               booktabs = T) %>%
+  kable_styling(full_width = T, latex_options = "hold_position")
+```
+
+However, the survey suggests something different, we can see that people who is older than 65 years old are much more concerned about climate change than the younger generations.
+
+### Household income
+
+We will also take a look at how household income affect people's opinion on global climate change.
+In this survey, income are separated into 6 different categories: *Under $40,000*, *$40,001 to $60,000*, *$60,001 to $80,000*, *$80,001 to $100,000*, *$100,001 to $150,000*, *More than $150,000*.
+Because this will be used as an input to the statistical model, we will simplify those ranges by taking its median, therefore, those range will become: *$30000*, *$50000*, *$70000*, *$90000*, *$125000*, *$200000*.
+(The Under 50000 and over 150000 are slightly adjusted).
+Figure \@ref(fig:incomeconcern) is a summary table.
+
+```{r incomeconcern, fig.cap='Concern about Climate Change Based on Household Income', echo=FALSE, warning=FALSE, message = FALSE, fig.width=5, fig.height=4, fig.pos = "!H"}
+income_relevant_data <- subset(climate_perception, select = c(`QD6`, `Q1r1`))
+names(income_relevant_data)[names(income_relevant_data) == 'QD6'] <- 'Household Income'
+names(income_relevant_data)[names(income_relevant_data) == 'Q1r1'] <- 'Concern'
+
+income_relevant_data <- income_relevant_data %>% filter(!str_detect(`Household Income`, "P"))
+income_relevant_data <- income_relevant_data %>% filter(!str_detect(`Concern`, "D"))
+
+income_relevant_data$`Concern`[income_relevant_data$`Concern`=="Extremely concerned"] <- "Concerned"
+income_relevant_data$`Concern`[income_relevant_data$`Concern`=="Very concerned"] <- "Concerned"
+
+income_relevant_data$`Concern`[income_relevant_data$`Concern`=="Not very concerned"] <- "Not Concerned"
+income_relevant_data$`Concern`[income_relevant_data$`Concern`=="Not at all concerned"] <- "Not Concerned"
+
+income_relevant_data$`Household Income`[income_relevant_data$`Household Income`=="Under $40,000"] <- 30000
+income_relevant_data$`Household Income`[income_relevant_data$`Household Income`=="$100,001 to $150,000"] <- 125000
+income_relevant_data$`Household Income`[income_relevant_data$`Household Income`=="More than $150,000"] <- 200000
+income_relevant_data$`Household Income`[income_relevant_data$`Household Income`=="$40,001 to $60,000"] <- 50000
+income_relevant_data$`Household Income`[income_relevant_data$`Household Income`=="$80,001 to $100,000"] <- 90000
+income_relevant_data$`Household Income`[income_relevant_data$`Household Income`=="$60,001 to $80,000"] <- 70000
+
+final_income_relevant_data <- income_relevant_data %>% group_by(`Household Income`, `Concern`) %>% 
+    summarize(n=n())
+
+final_income_relevant_data <- group_by(final_income_relevant_data, `Household Income`) %>% transmute(Concern, percent = round(n/sum(n),2))
+
+final_income_relevant_data %>%
+  knitr::kable(caption = "Concern about Climate Change Based on Household income",
+               col.names = c("Household Income", "Cocern Level", "Percentage WRT Household Income"),
+               align = c('l', 'l', 'l'),
+               booktabs = T) %>%
+  kable_styling(full_width = T, latex_options = "hold_position")
+```
+
+From the table, residents that are most concerned about climate change are people with household income between 80K and 100K.
 

### 2022-04-23 outputs/paper/paper.Rmd
finished everything other than discussion

@@
 knitr::opts_chunk$set(echo = TRUE)
+library(modelsummary)
 library(tidyverse)
@@
 library(plotrix)
+library(gt)
 # Read the dataset, use here to navigate to working directory
@@
 
-#annual_energy_2011 <- read_csv(here::here("inputs/data/energy-2011.csv"))
-#annual_energy_2012 <- read_csv(here::here("inputs/data/energy-2012.csv"))
-#annual_energy_2013 <- read_csv(here::here("inputs/data/energy-2013.csv"))
-#annual_energy_2014 <- read_csv(here::here("inputs/data/energy-2014.csv"))
-#annual_energy_2015 <- read_csv(here::here("inputs/data/energy-2015.csv"))
-#annual_energy_2016 <- read_csv(here::here("inputs/data/energy-2016.csv"))
-#annual_energy_2017 <- read_csv(here::here("inputs/data/energy-2017.csv"))
-#annual_energy_2018 <- read_csv(here::here("inputs/data/energy-2018.csv"))
 climate_perception <- read_csv(here::here("inputs/data/survey.csv"))
@@
 All survey respondents are adult residents living in the City of Toronto.
+
+## Data Overview
 All respondents are from 4 geological areas: Etobicoke-York, North York, Scarborough, and Toronto and East York, Figure \@ref(fig:respondents-number) is a bar graph showing the number of respondents from each area.
-
-```{r respondents-number, fig.cap='Number of Respondents from Each Area', echo=FALSE, warning=FALSE, message = FALSE, fig.width=5, fig.height=3, fig.pos = "!H"}
-number_from_each_area <- c(99, 101, 91, 113)
-area_name <- c("Etobicoke-York", "North York", "Scarborough", "Toronto and East York")
-ggplot() + geom_bar(aes(x=area_name,y=number_from_each_area), stat='identity') + xlab('Area') + ylab('Number of Respondents')
-```
-
 Other than coming from different city areas, respondents also have different demographic backgrounds, For instance, some respondents have a household income of more than $150000 while some respondents only have a household income lower than $40000.
@@
 Finally, Figure \@ref(fig:edulevel) shows the distribution of respondents based on their level of education.
+
+```{r respondents-number, fig.cap='Number of Respondents from Each Area', echo=FALSE, warning=FALSE, message = FALSE, fig.width=5, fig.height=2.5, fig.pos = "!H"}
+number_from_each_area <- c(99, 101, 91, 113)
+area_name <- c("Etobicoke-York", "North York", "Scarborough", "Toronto and East York")
+ggplot() + geom_bar(aes(x=area_name,y=number_from_each_area), stat='identity') + xlab('Area') + ylab('Number of Respondents')
+```
 
@@
 
-```{r incomesum, fig.cap='Number of Respondents Based on Household Income', echo=FALSE, warning=FALSE, message = FALSE, fig.width=5, fig.height=3, fig.pos = "!H"}
+```{r incomesum, fig.cap='Number of Respondents Based on Household Income', echo=FALSE, warning=FALSE, message = FALSE, fig.width=4, fig.height=4}
 
@@
 
+\newpage
+# Models
+
+Since our goal is to find out the impacts of demographic factors such as age, gender, income and education on one's awareness of global climate change.
+We will build a statistical model which takes those demographic factor as input, and output a binary variable indicating if this person will be concerned about climate change.
+The model will behave like the following where $\alpha_i$ denotes the $i^{th}$ demographic factor.
+
+$$f(\alpha_0, \alpha_1, \alpha_2, \alpha_3 ...) = 0\;or\;1$$
+
+## Logistic Regresssion
+
+Logistic regression is used when the dependent variable (target variable) is categorical, this fits perfectly here because our target variable is either *Concerned about Climate Change* or *Not Concerned about Climate Change*.
+Logistic regression is very similar to the traditional linear regression but it uses the regression formula inside the logistic function of ${\frac{e^x} {(1 + e^x)}}$, so it has the following form.
+
+$$P = {\frac{e^{(\beta_0 + \beta_1X_1)}}{1 + e^{(\beta_0 + \beta_1X_1)}}}$$
+However, in our case, since we have several independent variables, we can instead use Multiple Logistic Regression, it has the following form
+
+$$P = {\frac{e^{(\beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + ... + \beta_iX_i)}}{1 + e^{(\beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + ... + \beta_iX_i)}}}$$
+
+## Independent Variables
+
+For our statistical model, we will try to predict whether a person will be concerned with climate change using 4 demographic factors: Age, Gender, Income, and Level of Education.
+
+### Age
+
+We will investigate on whether a person's age has any effects on shaping his/her view on the global climate change.
+
+### Gender
+
+Because the vast majority respondents' gender is male or female.
+We will neglect other gender in this paper.
+Because gender is used as an input to the logistic regression model, we will use 1 to represent Male and 2 to represent Female.
+
+### Income
+
+The survey divides people's household income into 4 subgroups: *Under $40,000*, *$40,001 to $60,000*, *$60,001 to $80,000*, *$80,001 to $100,000*, *$100,001 to $150,000*, *More than $150,000*.
+We will use *$30000*, *$50000*, *$70000*, *$90000*, *$125000*, *$200000* to represent them respectively.\
+
+### Level of Education
+
+We will divide people's level of education into 3 groups: *High School or Less*, *Undergraduate Degree*, *Post Graduate Degree/Professional School*.
+We will use number 1 to 3 to represent each one of them respectively.
+
+Above is a summary of the model and indepedent variables we will be using, more details will be presented in the Results section.
+
+# Results
+
+We will first talk about each independent variable in more detail.
+
 ## Relationship between People's Awareness of Climate Change and Various Demographic Factors
@@
 Our ultimate goal is to develop a statistical model which takes a person's demographic factor as input, and try to predict whether that person will be concerned about global climate change.
-To do this, we will first take a look at different demographic factors, and determine whether it is relevant.
+To do this, we will take a look at different demographic factors, and determine their impacts in the model.
 
@@
 For simplicity, we will group *Extremely concerned* and *Very concerned* into a big category called *Concerned*, and we will group *Not very concerned* and *Not at all concerned* into a big category called *Not Concerned*, we will neglect *Don't know* answers.
-Figure \@ref(fig:ageconcern) is a summary table.
+Table \@ref(tab:ageconcern) is a summary table.
+However, the table suggests something different, we can see that people who is older than 65 years old are much more concerned about climate change than the younger generations.
 
@@
 
-However, the survey suggests something different, we can see that people who is older than 65 years old are much more concerned about climate change than the younger generations.
-
 ### Household income
@@
 (The Under 50000 and over 150000 are slightly adjusted).
-Figure \@ref(fig:incomeconcern) is a summary table.
+Table \@ref(tab:incomeconcern) is a summary table.
+From the table, residents that are most concerned about climate change are people with household income between 80K and 100K.
 
@@
 
-From the table, residents that are most concerned about climate change are people with household income between 80K and 100K.
+### Gender
 
-# Results
+We will now take a look at how people's gender affect their opinion on global climate change.
+The survey provides 5 options: *Woman*, *Man*, *Transgender*, *Prefer not to say*, *Not listed above*, since the vast majority respondents indicated their gender to be either *Man* or *Woman*, we will neglect the rest.
+For simplicity, we will use 1 to represent Male and 2 to represent Female.
+Table \@ref(tab:genderconcern) is a summary table.
+From the results, we can see that female are usually more concerned about climate change than males.
 
-# Discussion
+```{r genderconcern, fig.cap='Concern about Climate Change Based on Gender', echo=FALSE, warning=FALSE, message = FALSE, fig.width=5, fig.height=4, fig.pos = "!H"}
+
+gender_relevant_data <- subset(climate_perception, select = c(`QS2`, `Q1r1`))
+names(gender_relevant_data)[names(gender_relevant_data) == 'QS2'] <- 'Gender'
+names(gender_relevant_data)[names(gender_relevant_data) == 'Q1r1'] <- 'Concern'
+
+gender_relevant_data <- gender_relevant_data %>% filter(!str_detect(`Concern`, "D"))
+gender_relevant_data <- gender_relevant_data %>% filter(!str_detect(`Gender`, "P"))
+gender_relevant_data <- gender_relevant_data %>% filter(!str_detect(`Gender`, "T"))
+
+gender_relevant_data$`Concern`[gender_relevant_data$`Concern`=="Extremely concerned"] <- "Concerned"
+gender_relevant_data$`Concern`[gender_relevant_data$`Concern`=="Very concerned"] <- "Concerned"
+
+gender_relevant_data$`Concern`[gender_relevant_data$`Concern`=="Not very concerned"] <- "Not Concerned"
+gender_relevant_data$`Concern`[gender_relevant_data$`Concern`=="Not at all concerned"] <- "Not Concerned"
+
+gender_relevant_data$`Gender`[gender_relevant_data$`Gender` == "Man"] <- 1
+gender_relevant_data$`Gender`[gender_relevant_data$`Gender` == "Woman"] <- 2
+
+final_gender_relevant_data <- gender_relevant_data %>% group_by(`Gender`, `Concern`) %>% 
+    summarize(n=n())
+
+final_gender_relevant_data <- group_by(final_gender_relevant_data, `Gender`) %>% transmute(Concern, percent = round(n/sum(n),2))
+
+final_gender_relevant_data %>%
+  knitr::kable(caption = "Concern about Climate Change Based on Gender",
+               col.names = c("Gender", "Cocern Level", "Percentage WRT Gender"),
+               align = c('l', 'l', 'l'),
+               booktabs = T) %>%
+  kable_styling(full_width = T, latex_options = "hold_position")
+```
+
+### Level of Education
+
+Finally, we will look at the effect of education on people's awareness of climate change.
+There are 6 valid responses, for simplicity, we categorize them into 3 groups: *High School or Less*, *Undergraduate Degree*, *Post Graduate Degree/Professional School*, we will label them from 1-3 respectively.
+Table \@ref(tab:educoncern) is a summary table.
+From the table, clearly people with a higher level of education are usually more concerned with the climate change.
+
+```{r educoncern, fig.cap='Concern about Climate Change Based on Level of Education', echo=FALSE, warning=FALSE, message = FALSE, fig.width=5, fig.height=4, fig.pos = "!H"}
+edu_relevant_data <- subset(climate_perception, select = c(`QD5`, `Q1r1`))
+names(edu_relevant_data)[names(edu_relevant_data) == 'QD5'] <- 'Education'
+names(edu_relevant_data)[names(edu_relevant_data) == 'Q1r1'] <- 'Concern'
+
+edu_relevant_data <- edu_relevant_data %>% filter(!str_detect(`Education`, "Prefer not to answer"))
+edu_relevant_data <- edu_relevant_data %>% filter(!str_detect(`Concern`, "D"))
+
+edu_relevant_data$`Concern`[edu_relevant_data$`Concern`=="Extremely concerned"] <- "Concerned"
+edu_relevant_data$`Concern`[edu_relevant_data$`Concern`=="Very concerned"] <- "Concerned"
+
+edu_relevant_data$`Concern`[edu_relevant_data$`Concern`=="Not very concerned"] <- "Not Concerned"
+edu_relevant_data$`Concern`[edu_relevant_data$`Concern`=="Not at all concerned"] <- "Not Concerned"
+
+edu_relevant_data$`Education`[edu_relevant_data$`Education`=="High school or less"] <- 1
+edu_relevant_data$`Education`[edu_relevant_data$`Education`=="Some community college, vocational, trade school"] <- 2
+edu_relevant_data$`Education`[edu_relevant_data$`Education`=="Some university"] <- 2
+edu_relevant_data$`Education`[edu_relevant_data$`Education`=="Completed community college, vocational, trade school"] <- 2
+edu_relevant_data$`Education`[edu_relevant_data$`Education`=="Completed undergraduate degree"] <- 2
+edu_relevant_data$`Education`[edu_relevant_data$`Education`=="Post graduate/professional school"] <- 3
+
+final_edu_relevant_data <- edu_relevant_data %>% group_by(`Education`, `Concern`) %>% 
+    summarize(n=n())
+
+final_edu_relevant_data <- group_by(final_edu_relevant_data, `Education`) %>% transmute(Concern, percent = round(n/sum(n),2))
+
+final_edu_relevant_data %>%
+  knitr::kable(caption = "Concern about Climate Change Based on Level of Education",
+               col.names = c("Education", "Cocern Level", "Percentage WRT Education"),
+               align = c('l', 'l', 'l'),
+               booktabs = T) %>%
+  kable_styling(full_width = T, latex_options = "hold_position")
+```
+
+## Model Results
+
+We will now fit the data, Figure \@ref(fig:figmodel) shows the table of model results, it is produced by model summary [@modelsum].
+
+```{r, echo = FALSE, message = FALSE, warning = FALSE}
+
+# We are using 1, 2, 3, 4 to represent categories instead of using $30000 for example.
+# This is because we want all indepdent variable to be the same scale.
+all_relevant_data <- subset(climate_perception, select = c(`HIDAGE1`, `QD6`, `QS2`, `QD5`, `Q1r1`))
+names(all_relevant_data)[names(all_relevant_data) == 'Q1r1'] <- 'Concern'
+names(all_relevant_data)[names(all_relevant_data) == 'QD6'] <- 'Income'
+names(all_relevant_data)[names(all_relevant_data) == 'QS2'] <- 'Gender'
+names(all_relevant_data)[names(all_relevant_data) == 'QD5'] <- 'Education'
+names(all_relevant_data)[names(all_relevant_data) == 'HIDAGE1'] <- 'Age'
+
+# Filter out Don't know answers
+all_relevant_data <- all_relevant_data %>% filter(!str_detect(`Concern`, "D"))
+all_relevant_data <- all_relevant_data %>% filter(!str_detect(`Income`, "P"))
+all_relevant_data <- all_relevant_data %>% filter(!str_detect(`Gender`, "P"))
+all_relevant_data <- all_relevant_data %>% filter(!str_detect(`Gender`, "T"))
+all_relevant_data <- all_relevant_data %>% filter(!str_detect(`Education`, "Prefer not to answer"))
+
+# Transform Concern to Binary Variable
+all_relevant_data$`Concern`[all_relevant_data$`Concern`=="Extremely concerned"] <- 1
+all_relevant_data$`Concern`[all_relevant_data$`Concern`=="Very concerned"] <- 1
+
+all_relevant_data$`Concern`[all_relevant_data$`Concern`=="Not very concerned"] <- 0
+all_relevant_data$`Concern`[all_relevant_data$`Concern`=="Not at all concerned"] <- 0
+
+all_relevant_data$`Age`[all_relevant_data$`Age` >= 18 & all_relevant_data$`Age` < 25] <- 1
+all_relevant_data$`Age`[all_relevant_data$`Age` >= 25 & all_relevant_data$`Age` < 40] <- 2
+all_relevant_data$`Age`[all_relevant_data$`Age` >= 40 & all_relevant_data$`Age` < 55] <- 3
+all_relevant_data$`Age`[all_relevant_data$`Age` >= 55 & all_relevant_data$`Age` < 65] <- 4
+all_relevant_data$`Age`[all_relevant_data$`Age` >= 65 & all_relevant_data$`Age` < 150] <- 5
+
+all_relevant_data$`Income`[all_relevant_data$`Income`=="Under $40,000"] <- 1
+all_relevant_data$`Income`[all_relevant_data$`Income`=="$100,001 to $150,000"] <- 2
+all_relevant_data$`Income`[all_relevant_data$`Income`=="More than $150,000"] <- 3
+all_relevant_data$`Income`[all_relevant_data$`Income`=="$40,001 to $60,000"] <- 4
+all_relevant_data$`Income`[all_relevant_data$`Income`=="$80,001 to $100,000"] <- 5
+all_relevant_data$`Income`[all_relevant_data$`Income`=="$60,001 to $80,000"] <- 6
+
+all_relevant_data$`Gender`[all_relevant_data$`Gender` == "Man"] <- 1
+all_relevant_data$`Gender`[all_relevant_data$`Gender` == "Woman"] <- 2
+
+all_relevant_data$`Education`[all_relevant_data$`Education`=="High school or less"] <- 1
+all_relevant_data$`Education`[all_relevant_data$`Education`=="Some community college, vocational, trade school"] <- 2
+all_relevant_data$`Education`[all_relevant_data$`Education`=="Some university"] <- 2
+all_relevant_data$`Education`[all_relevant_data$`Education`=="Completed community college, vocational, trade school"] <- 2
+all_relevant_data$`Education`[all_relevant_data$`Education`=="Completed undergraduate degree"] <- 2
+all_relevant_data$`Education`[all_relevant_data$`Education`=="Post graduate/professional school"] <- 3
+
+all_relevant_data$Income <- as.numeric(as.character(all_relevant_data$Income))
+all_relevant_data$Gender <- as.numeric(as.character(all_relevant_data$Gender))
+all_relevant_data$Education <- as.numeric(as.character(all_relevant_data$Education))
+all_relevant_data$Concern <- as.numeric(as.character(all_relevant_data$Concern))
+
+logis_reg <- glm(Concern ~ Age + Gender + Education + Income,
+                         data = all_relevant_data, family = "binomial")
+
+```
+
+```{r figmodel, echo = FALSE, fig.cap='Model Summary',fig.align="center", out.height = "250px", out.width = "250px"}
+# call modelsummary(logis_reg) for the same result
+knitr::include_graphics("./model_result.png")
+```
+
+# References

### 2022-04-26 outputs/paper/paper.Rmd
finished project, added comment and appendix

@@
 ---
-title: "Toronto's Reaction to Fight Against Global Warming"
+title: "Woman and People with High Level of Education are More Concerend About Global Climate Change"
 author: 
@@
 The majority of the Science Community believes that global warming is caused by the excessive emission of greenhouse gases such as Carbon Dioxide and Methane.
-Luckily, people are getting more and more aware of the global change and are willing to make changes.
+Luckily, people are getting more and more aware of the global climate change and are willing to make changes.
 In this paper, we obtain a survey conducted on Toronto's residents about their perceptions of climate change and their willingness to take action on it.
-We aim to find out the impact of demographic factors such as personal income on people's perception of climate change."
+We aim to find out the impact of demographic factors such as personal income on people's perception of climate change.
+After careful investigation, we found out that woman and highly educated people are most concerned about climate change.
+Our findings can help the government to design better strategies to fight against global warming.\\par
+ \\textbf{Keywords:} Climate Change, Demographic Factor, Gender, Income, Education, Age, Concern, Model"
 output:
@@
 
+# group by year and draw the plot
 Land_Avg_sum <- cleaned_avg_temp %>% 
@@
 From the above two figures, it is very clear that the Earth's temperature is increasing rapidly after the Industrial Revolution.
-Based on research, Earth's temperature has risen by 0.08 Celsius per decade since 1880, and the rate of warming over the past 40 years is more than twice of that, 0.18 Celsius per decade.
+Based on research, Earth's ocean temperature has risen by 0.08 Celsius per decade since 1880, and the rate of warming over the past 40 years is more than twice of that, 0.18 Celsius per decade.
 People might develop the illusion that because this looks like a very small increase, it will have little or no impact on Earth's environment.
@@
 Toronto, for example, proposed an ambitious plan called TransformTO, its goal is to achieve net-zero greenhouse gas emissions.
-However, everyone has a different level of education, hence it is common for people to hold different opinions about climate change.
+However, everyone is different, hence it is common for people to hold different opinions about climate change.
 It is reasonable to believe that a university student majoring in environmental science will be more concerned about global warming than someone with high school education.
@@
 On top of that, the report written by the City of Toronto was also helpful [@report].
+After running a series of analysis on the survey, we found out that woman and highly educated people are most concerned about the global climate change.
 
@@
 ## Data Source and Collection
-The dataset I will be using are from the City of Toronto Data Portal, it is conducted city-wide to gather people's opinion on climate change [@opendatator], the goal of this survey is to capture their perceptions about climate change and to estimate people's willingness to take actions and help the city government to establish the goal of achieving net-zero carbon dioxide emission.
+The dataset I will be using is from the City of Toronto Data Portal, it is conducted city-wide to gather people's opinions on climate change [@opendatator], the goal of this survey is to capture their perceptions about climate change and to estimate people's willingness to take actions and help the city government to establish the goal of achieving net-zero carbon dioxide emission.
 The survey is conducted online and a total of 404 results were received between October 11 to October 18, 2018.
@@
 ## Data Overview
-All respondents are from 4 geological areas: Etobicoke-York, North York, Scarborough, and Toronto and East York, Figure \@ref(fig:respondents-number) is a bar graph showing the number of respondents from each area.
+All respondents are from 4 geological areas: Etobicoke-York, North York, Scarborough, Toronto and East York, Figure \@ref(fig:respondents-number) is a bar graph showing the number of respondents from each area.
 Other than coming from different city areas, respondents also have different demographic backgrounds, For instance, some respondents have a household income of more than $150000 while some respondents only have a household income lower than $40000.
@@
 age_of_all_respondents <- age_of_all_respondents["HIDAGE1"]
+
+# We will categorize age into 6 different groups by using the mutate function
 age_group <- age_of_all_respondents %>% mutate(cuts = cut(HIDAGE1, c(17, 25, 40, 55, 65, 150))) %>% 
@@
 
+# Change Column name
 levels(age_group$cuts) <- c("18 to 25", "25 to 40", "40 to 55", "55 to 65", "65+")
@@
 
+# Group responses by income range
 respondents_grouped_by_income <-
@@
 
+# Plot the summary
 ggplot(data=respondents_grouped_by_income, aes(x = reorder(`QD6`, n), y=n)) +
@@
 
+# Group response by people's level of education
 respondents_grouped_by_education <-
@@
 
+# Change column names and plot the data.
 names(respondents_grouped_by_education)[names(respondents_grouped_by_education) == 'n()'] <- 'n'
@@
 Since our goal is to find out the impacts of demographic factors such as age, gender, income and education on one's awareness of global climate change.
-We will build a statistical model which takes those demographic factor as input, and output a binary variable indicating if this person will be concerned about climate change.
+We will build a statistical model which takes that demographic factor as input and output a binary variable indicating if this person will be concerned about climate change.
 The model will behave like the following where $\alpha_i$ denotes the $i^{th}$ demographic factor.
@@
 The survey divides people's household income into 4 subgroups: *Under $40,000*, *$40,001 to $60,000*, *$60,001 to $80,000*, *$80,001 to $100,000*, *$100,001 to $150,000*, *More than $150,000*.
-We will use *$30000*, *$50000*, *$70000*, *$90000*, *$125000*, *$200000* to represent them respectively.\
+We will use numbers 1 through 6 to represent them respectively.
 
@@
 We will divide people's level of education into 3 groups: *High School or Less*, *Undergraduate Degree*, *Post Graduate Degree/Professional School*.
-We will use number 1 to 3 to represent each one of them respectively.
+We will use numbers 1 to 3 to represent each one of them respectively.
 
-Above is a summary of the model and indepedent variables we will be using, more details will be presented in the Results section.
+Above is a summary of the model and all the independent variables we will be using, more details will be presented in the Results section.
 
@@
 
-Our ultimate goal is to develop a statistical model which takes a person's demographic factor as input, and try to predict whether that person will be concerned about global climate change.
-To do this, we will take a look at different demographic factors, and determine their impacts in the model.
+Our ultimate goal is to develop a statistical model which takes a person's demographic factor as input and tries to predict whether that person will be concerned about global climate change.
+To do this, we will take a look at different demographic factors, and determine their impacts on the model.
 
@@
 Table \@ref(tab:ageconcern) is a summary table.
-However, the table suggests something different, we can see that people who is older than 65 years old are much more concerned about climate change than the younger generations.
+However, the table suggests something different, we can see that people who are older than 65 years old are much more concerned about climate change than the younger generations.
 
 ```{r ageconcern, fig.cap='Concern about Climate Change Based on Age Group', echo=FALSE, warning=FALSE, message = FALSE, fig.width=5, fig.height=4, fig.pos = "!H"}
+
+# Select column and change their name
 age_relevant_data <- subset(climate_perception, select = c(`HIDAGE1`, `Q1r1`))
@@
 
+# Group concern level into 2 big groups
 age_relevant_data$`Concern`[age_relevant_data$`Concern`=="Extremely concerned"] <- "Concerned"
@@
 
+# Categorize age into 6 age ranges
 final_age_relevant_data <- age_relevant_data %>% mutate(cuts = cut(Age, c(17, 25, 40, 55, 65, 150))) %>% group_by(cuts, Concern) %>% 
@@
 
+# Change column name and plot the data
 levels(final_age_relevant_data$cuts) <- c("18 to 25", "25 to 40", "40 to 55", "55 to 65", "65+")
@@
 
-We will also take a look at how household income affect people's opinion on global climate change.
+We will also take a look at how household income affects people's opinions on global climate change.
 In this survey, income are separated into 6 different categories: *Under $40,000*, *$40,001 to $60,000*, *$60,001 to $80,000*, *$80,001 to $100,000*, *$100,001 to $150,000*, *More than $150,000*.
-Because this will be used as an input to the statistical model, we will simplify those ranges by taking its median, therefore, those range will become: *$30000*, *$50000*, *$70000*, *$90000*, *$125000*, *$200000*.
+Because this will be used as an input to the statistical model, we will simplify those ranges by representing them with numbers 1 to 6 respectively.
 (The Under 50000 and over 150000 are slightly adjusted).
 Table \@ref(tab:incomeconcern) is a summary table.
-From the table, residents that are most concerned about climate change are people with household income between 80K and 100K.
+From the table, residents that are most concerned about climate change are people with household incomes between 80K and 100K.
 
 ```{r incomeconcern, fig.cap='Concern about Climate Change Based on Household Income', echo=FALSE, warning=FALSE, message = FALSE, fig.width=5, fig.height=4, fig.pos = "!H"}
+
+# Select column and change their name
 income_relevant_data <- subset(climate_perception, select = c(`QD6`, `Q1r1`))
@@
 
+# Filter out invalid responses
 income_relevant_data <- income_relevant_data %>% filter(!str_detect(`Household Income`, "P"))
@@
 
+# Group concern level into 2 big groups
 income_relevant_data$`Concern`[income_relevant_data$`Concern`=="Extremely concerned"] <- "Concerned"
@@
 
+# Group concern level into 2 big groups
 income_relevant_data$`Concern`[income_relevant_data$`Concern`=="Not very concerned"] <- "Not Concerned"
@@
 
+# Take the median of different income group 
 income_relevant_data$`Household Income`[income_relevant_data$`Household Income`=="Under $40,000"] <- 30000
@@
 
+# Group by and calculate the percentanges
 final_income_relevant_data <- group_by(final_income_relevant_data, `Household Income`) %>% transmute(Concern, percent = round(n/sum(n),2))
 
+# Plot the data
 final_income_relevant_data %>%
@@
 
-We will now take a look at how people's gender affect their opinion on global climate change.
-The survey provides 5 options: *Woman*, *Man*, *Transgender*, *Prefer not to say*, *Not listed above*, since the vast majority respondents indicated their gender to be either *Man* or *Woman*, we will neglect the rest.
-For simplicity, we will use 1 to represent Male and 2 to represent Female.
+We will now take a look at how people's gender affects their opinion on global climate change.
+The survey provides 5 options: *Woman*, *Man*, *Transgender*, *Prefer not to say*, *Not listed above*, since the vast majority of respondents indicated their gender to be either *Man* or *Woman*, we will neglect the rest.
+For simplicity, we will use 1 to represent males and 2 to represent females.
 Table \@ref(tab:genderconcern) is a summary table.
-From the results, we can see that female are usually more concerned about climate change than males.
+From the results, we can see that females are usually more concerned about climate change than males.
 
@@
 
+# Very similar to the previous code block
 gender_relevant_data <- subset(climate_perception, select = c(`QS2`, `Q1r1`))
@@
 
+# Filter out invalid responses
 gender_relevant_data <- gender_relevant_data %>% filter(!str_detect(`Concern`, "D"))
@@
 
+# Group concern level into 2 big groups
 gender_relevant_data$`Concern`[gender_relevant_data$`Concern`=="Extremely concerned"] <- "Concerned"
@@
 
+# Group concern level into 2 big groups
 gender_relevant_data$`Concern`[gender_relevant_data$`Concern`=="Not very concerned"] <- "Not Concerned"
@@
 
+# Use 1 to represent man and 2 to represent woman
 gender_relevant_data$`Gender`[gender_relevant_data$`Gender` == "Man"] <- 1
@@
 
+# Plot the data
 final_gender_relevant_data %>%
@@
 Table \@ref(tab:educoncern) is a summary table.
-From the table, clearly people with a higher level of education are usually more concerned with the climate change.
+From the table, people with a higher level of education are usually more concerned with climate change.
 
 ```{r educoncern, fig.cap='Concern about Climate Change Based on Level of Education', echo=FALSE, warning=FALSE, message = FALSE, fig.width=5, fig.height=4, fig.pos = "!H"}
+
+# Similar to previous code block
 edu_relevant_data <- subset(climate_perception, select = c(`QD5`, `Q1r1`))
@@
 
+# Represent education by number
 edu_relevant_data$`Education`[edu_relevant_data$`Education`=="High school or less"] <- 1
@@
 
+# Plot the data
 final_edu_relevant_data %>%
@@
 
-```{r, echo = FALSE, message = FALSE, warning = FALSE}
+```{r, include = FALSE, echo = FALSE, message = FALSE, warning = FALSE}
 
@@
 all_relevant_data$`Income`[all_relevant_data$`Income`=="Under $40,000"] <- 1
-all_relevant_data$`Income`[all_relevant_data$`Income`=="$100,001 to $150,000"] <- 2
-all_relevant_data$`Income`[all_relevant_data$`Income`=="More than $150,000"] <- 3
-all_relevant_data$`Income`[all_relevant_data$`Income`=="$40,001 to $60,000"] <- 4
-all_relevant_data$`Income`[all_relevant_data$`Income`=="$80,001 to $100,000"] <- 5
-all_relevant_data$`Income`[all_relevant_data$`Income`=="$60,001 to $80,000"] <- 6
+all_relevant_data$`Income`[all_relevant_data$`Income`=="$40,001 to $60,000"] <- 2
+all_relevant_data$`Income`[all_relevant_data$`Income`=="$60,001 to $80,000"] <- 3
+all_relevant_data$`Income`[all_relevant_data$`Income`=="$80,001 to $100,000"] <- 4
+all_relevant_data$`Income`[all_relevant_data$`Income`=="$100,001 to $150,000"] <- 5
+all_relevant_data$`Income`[all_relevant_data$`Income`=="More than $150,000"] <- 6
 
@@
 
+# Run the logistic regression
 logis_reg <- glm(Concern ~ Age + Gender + Education + Income,
                          data = all_relevant_data, family = "binomial")
+
+summary(logis_reg)
 
@@
 
+By taking a look at the summary statistic table, the most significant factor is gender, it has a P-value of 0.0004, this means it is very likely that gender is an important factor in determining whether a person will be concerned about global warming.
+The coefficient for gender is 1.16, since we use 1 to represent *Concern* and 0 to represent *Not Concern*, this implies that woman is usually more concerned about global climate change.
+Similarly, Education has a P value of 0.007 which also makes it to be a significant factor.
+Since we use a bigger number to represent a higher level of education, this means that people with a higher level of education are usually more concerned about climate change than people with a lower level of education.
+Finally, Age and Income have a high P-value, which means there is no sufficient evidence to suggest that they are key factors in determining whether someone will be concerned about climate change.
+
+# Discussion
+
+## What is Done in This Paper
+After investigating on climate perception survey provided by the City of Toronto, we found out that gender and education are key factors in determining whether a person will be concerned about climate change.
+First of all, we found that women are usually more concerned about global climate change than men.
+Women in developed countries are more likely to recycle, purchase organic food and eco-labelled products, and support energy-efficiency policies.
+According to European research, women are more concerned about climate change and are more willing to make sacrifices to reduce carbon emissions than men.
+In the United States, women are 5% more likely than men to believe in climate science[@one-earth].
+On top of that, women are also the most impacted group by climate change, it is estimated that 80% of people displaced by climate change are women.
+In less developed countries, women are usually responsible for gathering water and food, hence it is easier for them to feel the environmental degradation [@one-earth].
+
+Education is another key factor, our research shows that people with a higher level of education are more informed and concerned about climate change.
+The United Nations also stated that Education is the key to addressing climate change because education can help people change their attitudes and behaviours, as well as make more informed decisions.
+Young people can be taught about the effects of global warming and how to adapt to it in the classroom.
+Education can make people be more socially responsible and it can motivate the young people to take action against global warming [@united-nations].
+
+## Weakness and How to Improve
+
+The most notable weakness of this investigation is the sample size, the survey received a total of 404 responses, after filtering out invalid responses, we are left with 325 valid responses.
+Clearly, this sample size is too small, what we can do is sample more population by contacting more potential participants.
+This can also reduce bias in the result, currently, all of the participants indicated that their gender is either male or female, this means we are not receiving any feedback from sexual minority groups such as homosexual, bisexual and non-heterosexual individuals.
+
+Our statistical model also has potential problems because some independent variables are actually correlated.
+For example, education and income are two correlated variables because people with a higher level of education are more likely to have a higher income.
+This can be a significant problem because a change in one independent variable can results in the change of another independent variable, as a result, the model will fluctuate significantly.
+What we can do to solve this problem is to develop a more sophisticated statistical model.
+
+## What is Left to Learn and How Should We Proceed in the Future
+
+In our paper, we investigated each demographic factor separately without considering them as a whole.
+What we should explore next is to find out their interrelationship.
+For example, in this paper, we find out that age is not a key factor in determining one's awareness of climate change.
+However, it is possible that the combination of age and gender is a significant indicator.
+Table \@ref(tab:genderageconcern) is a summary table showing the number of people concerned about climate change, grouped by gender and age.
+Let us take a look at the age group 25-40 and 55-65.
+In the age group 25-40, 80% of people indicated that they are worried about climate change.
+Similarly, 80% of the population in the 55-65 age group indicated that they are worried about climate change, suggesting that age alone is not a determining factor.
+However, among all women with age between 25-40, 7% stated that they are not concerned about climate change, but among all women with age between 55-65, only 2% stated that they are not concerned about climate change, meaning that elder women are more concerned about climate change.
+This difference suggests that gender and age together might be a determining factor.
+
+```{r genderageconcern, fig.cap='Concern about Climate Change Based on Gender', echo=FALSE, warning=FALSE, message = FALSE, fig.width=5, fig.height=4, fig.pos = "!H"}
+
+# Group by gender and age
+gender_relevant_data <- subset(climate_perception, select = c(`QS2`, `Q1r1`, `HIDAGE1`))
+names(gender_relevant_data)[names(gender_relevant_data) == 'QS2'] <- 'Gender'
+names(gender_relevant_data)[names(gender_relevant_data) == 'Q1r1'] <- 'Concern'
+
+names(gender_relevant_data)[names(gender_relevant_data) == 'HIDAGE1'] <- 'Age'
+
+gender_relevant_data <- gender_relevant_data %>% filter(!str_detect(`Concern`, "D"))
+gender_relevant_data <- gender_relevant_data %>% filter(!str_detect(`Gender`, "P"))
+gender_relevant_data <- gender_relevant_data %>% filter(!str_detect(`Gender`, "T"))
+
+gender_relevant_data$`Concern`[gender_relevant_data$`Concern`=="Extremely concerned"] <- "Concerned"
+gender_relevant_data$`Concern`[gender_relevant_data$`Concern`=="Very concerned"] <- "Concerned"
+
+gender_relevant_data$`Concern`[gender_relevant_data$`Concern`=="Not very concerned"] <- "Not Concerned"
+gender_relevant_data$`Concern`[gender_relevant_data$`Concern`=="Not at all concerned"] <- "Not Concerned"
+
+gender_relevant_data$`Gender`[gender_relevant_data$`Gender` == "Man"] <- 1
+gender_relevant_data$`Gender`[gender_relevant_data$`Gender` == "Woman"] <- 2
+
+# Split age into different groups
+final_gender_relevant_data <- gender_relevant_data %>% mutate(cuts = cut(Age, c(17, 25, 40, 55, 65, 150)))
+
+final_gender_relevant_data <- final_gender_relevant_data %>% group_by(`Gender`, `cuts`, `Concern`) %>% 
+    summarize(n=n())
+
+# Plot the table
+final_gender_relevant_data %>%
+  knitr::kable(caption = "Concern about Climate Change Based on Gender and Age",
+               col.names = c("Gender", "Age Range", "Cocern Level", "Number"),
+               align = c('l', 'l', 'l'),
+               booktabs = T) %>%
+  kable_styling(full_width = T, latex_options = "hold_position")
+```
+
+\newpage
+
+# Appendix
+
+```{r, out.width='800px', echo=F, fig.pos = "!H"}
+knitr::include_graphics("../../inputs/data/s1.png")
+```
+
+```{r, out.width='800px', echo=F, fig.pos = "!H"}
+knitr::include_graphics("../../inputs/data/s2.png")
+```
+
+```{r, out.width='800px', echo=F, fig.pos = "!H"}
+knitr::include_graphics("../../inputs/data/s3.png")
+```
+
+```{r, out.width='800px', echo=F, fig.pos = "!H"}
+knitr::include_graphics("../../inputs/data/s4.png")
+```
+
+```{r, out.width='800px', echo=F, fig.pos = "!H"}
+knitr::include_graphics("../../inputs/data/s5.png")
+```
+
+```{r, out.width='800px', echo=F, fig.pos = "!H"}
+knitr::include_graphics("../../inputs/data/s6.png")
+```
+
+```{r, out.width='800px', echo=F, fig.pos = "!H"}
+knitr::include_graphics("../../inputs/data/s7.png")
+```
+
+\newpage
 # References

### 2022-04-26 outputs/paper/paper.Rmd
change repo name

@@
   - Lantao Cui
-thanks: "Code and data are available at: https://github.com/cuilantao/Toronto-s-reaction-to-fight-against-global-warming"
+thanks: "Code and data are available at: https://github.com/cuilantao/The-Impact-of-Demographic-Factors-on-People-s-Awareness-on-Climate-Change"
 date: "`r format(Sys.time(), '%d %B %Y')`"
